### 2022-07-12 report/rl_qf_report.tex
initial commit

\documentclass[11pt]{article}
\usepackage{amsmath, amsfonts, bm, listings, enumitem, geometry, titlesec,
array, makecell, caption, graphicx, float, algorithm, algpseudocode}
\usepackage[table]{xcolor}
\usepackage{tikz}
\usetikzlibrary{shapes.geometric, arrows.meta}
\usepackage{hyperref}
\geometry{margin=0.8in}
\graphicspath{ {./imgs/} }
%\renewcommand{\familydefault}{\sfdefault}

\tikzstyle{process} = [rectangle, minimum width=2cm, minimum height=1.3cm, 
text centered, draw=black]
\tikzstyle{arrow} = [thick,->,>={Stealth[scale=1.1]}]

\title{Reinforcement Learning Report}
\author{Yuanhao JIANG}
\date{}

\begin{document}
\maketitle
\tableofcontents

\section{Introduction}
The object is to use reinforcement learning to solve the following scenario:
a customer arrives with a number of features, we want to promote the customer
with a proper price, such that he is most likely to purchase our product, and 
we also have the highest profit and a better portfolio. 
\vspace{3mm}\newline We can consider this scenario as markov decision process,
with the current state being the current customer features and current 
portfolio. At each time step, the agent promote a price according to the 
current customer features and the current portfolio, after that the customer 
resopnse to the action. The reward is then given besed on the customer 
response and the portfolio. Then the portfolio updates and a new customer 
arrives.

\section{Reinforcement Learning}
The reinforcement learning method we want to use is based on the Markov 
decision process (MDP), as illustrated below:
\begin{center}
    \begin{tikzpicture}
        \node (agent) [process, minimum width=2cm, minimum height=2cm,
            label={[anchor=north,inner sep=5pt]north:Agent}]{};
        \node (pi) [process, left of=agent, minimum width=1cm, 
            minimum height=1cm,xshift=1cm, yshift=-0.3cm] {\(\pi\)};
        \node (env) [process, minimum height=1.5cm, below of=pi, yshift=-1cm] 
            {Environment};

        \draw [arrow] (env.163) -- ++(-1.5,0) node[anchor=south, xshift=0.8cm]
            {\(S_{t+1}\)} coordinate(a1);
        \draw [arrow] (a1) -- ++(-0.7,0) |- node[anchor=south, xshift=1.3cm] 
            {\(S_t\)} (pi);
        \draw [arrow] (env.197) -- ++(-1.5,0) node[anchor=south, xshift=0.8cm]
            {\(R_{t+1}\)} coordinate(a2);
        \draw [arrow] (a2) -- ++(-1.3,0) -- ++(0,3.2) 
            -- node[anchor=south, xshift=0.5cm] {\(R_t\)} (agent.154);
        \draw [arrow] (pi) -- ++(2.7,0) node[anchor=south, xshift=-0.8cm] 
            {\(A_t\)} |- (env);
        \draw [dashed,thick] (-2.7,-1.5) -- (-2.7, -3.2);
    \end{tikzpicture}

\end{center}
\noindent However, in RL, the agent is not told which actions to take, but 
instead must discover which actions yield the most reward by trying them. Our 
goal at each time step is to find a policy \(\pi\) to maximize the expected 
reward alonge the process afterwards, which is given by the value function
\[V(s)=\mathbb{E}\left[\sum_{i=0}^{\infty} \gamma^i R_{t+i+1}\;\middle|\; 
S_t=s\right]\]
To achieve this, we need to evaluate the current policy, and improve it 
accordingly.

\subsection{Policy Evaluation}
We want to evaluate the value function under a given policy \(\pi\). According 
to Bellman equation,
\[v_\pi(s)=\mathbb{E}_\pi\left[R_{t+1}+\gamma v_\pi(S_{t+1})\;\middle|\;
S_t=s\right]\]
We can use it to iteratively compute \(v_\pi\). The iteratively update is
\[v_{k+1}(s)=\mathbb{E}_\pi\left[R_{t+1}+\gamma v_k(S_{t+1})\;\middle|\;
S_t=s\right]\]
which is proven that it will converge to the true value given any initial value 
function.

\subsection{Policy Improvement}
Now we have the evaluated value function for the policy, we want to improve it
accordingly. To do this, we introduce the q-function under policy \(\pi\)
\[q_\pi(s, a) = \mathbb{E}\left[R_{t+1} + \gamma v_\pi(S_{t+1})\;\middle|\;
S_t=s, A_t=a\right]\]
The policy improvement theorem says that, let \(\pi\) and \(\pi'\) be any pair
of policy, for all \(s\) we have
\[q_\pi(s, \pi'(s))\geq v_\pi(s) \:\Rightarrow\: v_{\pi'}(s) \geq v_\pi(s)\]
Now we can improve the policy by
\[\pi'(s)=\underset{a}{\text{argmax}}\:q_\pi(s,a)\]
for all \(s\).

\subsection{Policy Iteration}
By iteratively applying policy evaluation and policy improvement, we can obtain
a sequence of monotonically improving policies and value functions:
\[\pi_0 \overset{E}{\longrightarrow} v_{\pi_0} \overset{I}{\longrightarrow}
\pi_1 \overset{E}{\longrightarrow} v_{\pi_1} \overset{I}{\longrightarrow}
\dots \overset{I}{\longrightarrow} \pi_* \overset{E}{\longrightarrow} v_*\]
where \(\overset{E}{\longrightarrow}\) denotes a policy evaluation and
\(\overset{I}{\longrightarrow}\) denotes a policy improvement. This way of 
finding an optimal policy is called policy iteration.
\subsection{Value Iteration}
One drawback to policy iteration is that each of its iterations involves policy
evaluation, which itself is a protracted iterative computation requiring 
multiple sweeps through the state set.
\vspace{3mm}\newline We now truncate the policy evaluation such that it is
stopped after just one sweep (one update of each state):
\begin{align*}
    v_{k+1}(s)&=\underset{a}{\text{max}}\:q(s, a)\\
              &=\underset{a}{\text{max}}\:\mathbb{E}\left[
          R_{t+1}+\gamma v_k(S_{t+1})\;\middle|\;S_t=s, A_t=a\right]
\end{align*}
We keep iterate until \(v\) converges (to \(v_*\)), then we record the last
policy \(\pi(s) = \underset{a}{\text{argmax}}\:q(s, a)\).

\subsection{Generalized Policy Iteration}
As long as both processes, policy evaluation and policy improvement, continue
to update all states, the ultimate result is typically the same --- converge to
the optimal value function and an optimal policy.
\vspace{3mm}\newline Generalized policy iteration (GPI) is used to refer to the
general idea of letting policy evaluation and policy improvement interact, 
independent of the granularity of the two processes (instead of letting each
complete before the other begins).

\subsection{Temporal-Difference Learning}
When we don't have the complete model of the environment, we need to estimate 
the value function from only experience. There are two methods to do so: 
Monte Carlo Methods and Temporal-Difference. We will use Temporal-Difference
method in this project.
\vspace{3mm}\newline To estimate \(v_\pi(S_t)\) using only the experience, we 
take the average on all experienced trajectory' values. Temporal-Difference
method uses \(G_i = [R_{t+1}]_i+\gamma [v_\pi(S_{t+1})]_i\) to estimate the 
value of the \(i\)th trajectory starting at \(S_t\), with \(v_\pi\) being the 
estimated value function at the \(i\)th time \(S_t\) is visitied, which can be 
initialized to anything at start. Now we have the incremental formula to update
our value function:
\begin{align*}
    [v_\pi(S_t)]_{k+1} &= \frac{1}{k}\sum_{i=1}^{k} G_i\\
               &= \frac{1}{k}\left(G_k + \sum_{i=1}^{k-1} G_i\right)\\
               &= \frac{1}{k}\left(G_k + (k-1)[v_\pi(S_t)]_{k}\right)\\
               &= [v_\pi(S_t)]_k + \frac{1}{k}(G_k-[v_\pi(S_t)]_k)\\
               &= [v_\pi(S_t)]_k + \frac{1}{k}
               ([R_{t+1}]_k+\gamma [v_\pi(S_{t+1})]_k-[v_\pi(S_t)]_k)
\end{align*}
To simplify:
\[v_\pi(S_t)\longleftarrow v_\pi(S_t)+\alpha
[R_{t+1}+\gamma v_\pi(S_{t+1})-v_\pi(S_t)]\]
with \(\alpha\) being the stepsize. And this also applies to the q function:
\[q_\pi(S_t, A_t)\longleftarrow q_\pi(S_t, A_t)+\alpha
[R_{t+1}+\gamma q_\pi(S_{t+1}, A_{t+1})-q_\pi(S_t, A_t)]\]

\subsection{Policy Gradient Methods}
When the state space is arbitrarily large, we cannot find an optimal policy or
the optimal value function given the limited resources and time. Instead of 
keeping track of the value and the action(s) to select for each state (tabular 
methods), we can use parameterized functions, for example, artificial neural 
networks (ANNs), to approximate the value function and the policy function. 
\vspace{3mm}\newline Previously methods learned the values of actions and then 
select actions based on their estimated action values (q function). Now we 
consider methods that instead learn a parameterized policy that select actions 
without consulting a value function. A value function may still be used to 
learn the policy parameter, but is not required for action selection.
\vspace{3mm}\newline We use \(\bm{\theta}\) and \(\bm{w}\) to denotes the 
policy's parameter vector and value function's weight vector, respectively.
Then we have our policy \(\pi\left(a\;\middle|\;s, \bm{\theta}\right)=
\text{Pr}\left\{A_t=a\;\middle|\;S_t=s, \bm{\theta_t}=\bm{\theta}\right\}\) and
value function \(v_\pi(s, \bm{w})\). We also define the scalar performance 
measure (objective) to be 
\[J(\bm{\theta})=\begin{cases}
    \ v_{\pi_{\bm{\theta}}}(s_0); &\text{episodic case}\\
    \ \lim_{t \to \infty} \mathbb{E}
    \left[R_t\;\middle|\;S_0,A_{0:t-1}\sim\pi\right];      
                                  & \text{continuing case}
\end{cases}\]
Policy gradient methods seeks to maximize this performance measure, so their 
updates approximate gradient ascent in \(J\):
\[\bm{\theta}_{t+1}=\bm{\theta}_t+\alpha\widehat{\nabla J(\bm{\theta}_t)}\]
where \(\widehat{\nabla J(\bm{\theta}_t)}\) is a stochastic estimate whose
expection approximates the gradient of the performance measure w.r.t 
\(\bm{\theta}_t\).

\subsubsection{The Policy Gradient Theorem}
The policy gradient theorem says
\[\nabla J(\bm{\theta})\propto \sum_{s} \mu(s) 
\sum_{a} q_\pi(s,a)\nabla\pi\left(a\middle|s, \bm{\theta}\right)\]
where \(\mu\) is the stationary distribution of the state. Thus we can derive
\begin{align*}
    \nabla J(\bm{\theta}) 
    &\propto \sum_{s} \mu(s) 
    \sum_{a} q_\pi(s,a)\nabla\pi\left(a\middle|s, \bm{\theta}\right)\\
    &= \mathbb{E}_\pi\left[\sum_{a} q_\pi(S_t,a)
    \nabla\pi\left(a\middle|S_t, \bm{\theta}\right)\right]\\
    &= \mathbb{E}_\pi\left[\sum_{a} \pi\left(a\middle|S_t, \bm{\theta}\right)
        q_\pi(S_t,a)\frac{\nabla\pi\left(a\middle|S_t, \bm{\theta}\right)}
        {\pi\left(a\middle|S_t, \bm{\theta}\right)}\right]\\
    &=\mathbb{E}_\pi\left[q_\pi(S_t,A_t)
        \frac{\nabla\pi\left(A_t\middle|S_t, \bm{\theta}\right)}
        {\pi\left(A_t\middle|S_t, \bm{\theta}\right)}\right]
\end{align*}
The policy gradient theorem can be generalized to include a comparison of the 
action value to an arbitrary baseline \(b(s)\):
\[\nabla J(\bm{\theta})\propto \sum_{s} \mu(s) \sum_{a} 
    \Bigl(q_\pi(s,a)-b(s)\Bigr)\nabla\pi\left(a\middle|s, \bm{\theta}\right)\]
with the same derivation we have
\[\nabla J(\bm{\theta})\propto\mathbb{E}_\pi\left[
        \Bigl(q_\pi(S_t,A_t)-b(S_t)\Big)
        \frac{\nabla\pi\left(A_t\middle|S_t, \bm{\theta}\right)}
{\pi\left(A_t\middle|S_t, \bm{\theta}\right)}\right]\]
One natural choice for baseline is an estimate of the state value, 
\(\hat{v}(S_t, \bm{w})\), where \(\bm{w}\) is the weight vector to be learned.

\subsubsection{Actor-Critic Methods}
Recall the TD method, we make use of 
\(q_\pi(s,a)=\mathbb{E}\left[R_{t+1}+\gamma v_\pi(S_{t+1})\;\middle|\;
S_t=s, A_t=a\right]\), by taking one sample estimate, and choosing
\(\hat{v}(S_t, \bm{w})\) as baseline, we have
\[\nabla J(\bm{\theta})\propto\mathbb{E}_\pi\left[
        \Bigl(R_{t+1}+\gamma \hat{v}(S_{t+1}, \bm{w})-\hat{v}(S_t, \bm{w})\Big)
        \frac{\nabla\pi\left(A_t\middle|S_t, \bm{\theta}\right)}
{\pi\left(A_t\middle|S_t, \bm{\theta}\right)}\right]\]
Again, by taking one sample estimate we have the update formula for 
\(\bm{\theta}\):
\begin{align*}
    \bm{\theta}_{t+1}
    &=\bm{\theta}_t + \alpha_{\bm{\theta}}
    \Bigl(R_{t+1}+\gamma \hat{v}(S_{t+1}, \bm{w})-\hat{v}(S_t, \bm{w})\Big)
    \frac{\nabla\pi\left(A_t\middle|S_t, \bm{\theta}_t\right)}
    {\pi\left(A_t\middle|S_t, \bm{\theta}_t\right)}\\
    &=\bm{\theta}_t+\alpha_{\bm{\theta}}\delta_t
    \nabla\ln{\pi\left(A_t\middle|S_t, \bm{\theta}_t\right)}
\end{align*}
As for the weight vector \(\bm{w}\) for the estimated value function, at each 
time step \(t\), we want to update it by minimizing the squared error,
\(\bigl[v_\pi(S_t)-\hat{v}(S_t, \bm{w}_t)\bigr]^2\):
\begin{align*}
    \bm{w}_{t+1} 
    &= \bm{w}_t - 
    \alpha_{\bm{w}}'\nabla \Bigl[v_\pi(S_t)-\hat{v}(S_t, \bm{w}_t)\Bigr]^2\\
    &= \bm{w}_t - \alpha_{\bm{w}}\Bigl(v_\pi(S_t)-\hat{v}(S_t, \bm{w}_t)
    \Bigr)\nabla \hat{v}(S_t, \bm{w}_t)
\end{align*}
where \(v_\pi\) is the true value function. Again, since \(v_\pi(s)=
\mathbb{E}\left[R_{t+1}+\gamma v_\pi(S_{t+1})\;\middle|\;S_t=s\right]\), we
take one sample estimate, which gives us the update formula for \(\bm{w}\):
\begin{align*}
    \bm{w}_{t+1} 
    &= \bm{w}_t - \alpha_{\bm{w}}
    \Bigl(R_{t+1}+\gamma\hat{v}(S_{t+1},\bm{w})-\hat{v}(S_t, \bm{w}_t)
    \Bigr)\nabla \hat{v}(S_t, \bm{w}_t)\\
    &=\bm{w}_t - \alpha_{\bm{w}}\delta_t\nabla \hat{v}(S_t, \bm{w}_t)
\end{align*}
The actor-critic method is based on the above updates formulas:
\begin{algorithm}
\caption{Actor-Critic}
\begin{algorithmic}[1]
\State Input: a differentiable policy parameterization 
\(\pi\left(a\middle|s, \bm{\theta}\right)\)
\State Input: a differentiable state-value function parameterization
\(\hat{v}(s,\bm{w})\)
\State Step sizes \(\alpha_{\bm{\theta}}>0\), \(\alpha_{\bm{w}}>0\)
\State \(\bm{\theta} \gets \bm{0}\), \(\bm{w} \gets \bm{0}\)
\Loop \hspace{0.3mm} (for each episode)
    \State Initialize \(S\) (first state of the episode)
    \State \(I \gets 1\)
    \Loop \hspace{0.3mm} (for each time step)
        \State \(A\sim\pi\left(\cdot\middle|S, \bm{\theta}\right)\)
        \State Take action \(A\), observe \(S'\), \(R\)
        \State \(\delta \gets R + \gamma\hat{v}(S',\bm{w})-\hat{v}(S,\bm{w})\)
        \State \(\bm{w} \gets \bm{w} + 
        \alpha_{\bm{w}} \delta\nabla\hat{v}(S,\bm{w})\)
        \State \(\bm{\theta} \gets \bm{\theta} + \alpha_{\bm{\theta}}I\delta
        \nabla\ln{\pi\left(A\middle|S, \bm{\theta}\right)}\)
        \State \(I \gets \gamma I\)
        \State \(S \gets S'\)
    \EndLoop
\EndLoop
\end{algorithmic}
\end{algorithm}

\section{Build the Environment}
The environment does the following things:
\begin{enumerate}
    \item record the current state that can be queried anytime
    \item when an action, i.e. a price, is given according to the current 
        state, it outputs the reward, and goes to next state
\end{enumerate}
At each time step, the state consists of a randomly generated customer's 
features and the current portfolio. After the agent performs an action, i.e.
promotes a price to the customer, the reward is then computed based on the 
profit on this customer and the portfolio up to now.

\subsection{Customer Features}
A customer' features is represented by an array (or vector), denoted by \(x\) 
with 15 entries with each generated randomly from a distribution, 
including normal distribution, binomial distribution, and so on. For example, 
a feature vector \(x\) is described as below:
\begin{table}[htpb]
    \centering
    \begin{tabular}{c|c|c|c|c|c|c|c}
        gender & age & car cost & miles & brand & random feature 0 & random 
        feature 1 & \dots\\
        \hline
        1.0 & 42.723 & 94032.096 & 30086.311 & 29.264 & 8.0 & 68.740 & \dots
    \end{tabular}
\end{table}

\noindent After a price, denoted by \(c\), is promoted to a customer, the 
customer will give a resopnse, denoted by \(r\), which is 0 if he does not buy
the product, and 1 otherwise. And the profit we have for that customer, 
denoted by pf, can be computed by
\[\text{pf} = r*\left(c - g(x)\right)\]
where \(g(x)\) is the cost on that customer.

\subsection{Resopnse}
The resopnse is generated by a generalized linear model, whose input is a 
vector of a customer features vector \(x\) appended with a price \(c\), i.e.
\(r=glm(x[0], \dots, x[14], c)\).
\vspace{3mm}\newline The GLM used in the project is fitted using a randomly
generated data set with each observation is a customer's features followed by 
a price, then followed by a resopnse e.g.
\begin{table}[htpb]
    \centering
    \begin{tabular}{c|c|c|c|c|c}
        & customer feature 0 & \dots & customer feature 14 & price & resopnse\\
        \hline
        1 & 1.0 & \dots & 3.278 & 1109.504 & 1.0\\
        \hline
        2 & 0.0 & \dots & 1.991 & 665.8 & 0.0\\
        \hline
        \dots & \dots & \dots & \dots & \dots & \dots
    \end{tabular}
\end{table}

\noindent And its link function is chose to be the logistic function.

\subsection{State}
The state at start of each time step is the feature vector of the new customer 
to promote, appended by the portfolio, which is also a data vector consists of
the following entries:
\begin{itemize}
    \item average profit over all customers so far, expect for the new customer
        at current time step, denoted by avg\_pf (initialized to \(0\)), 
        which is computed by
        \[\text{avg\_pf}_t = \frac{1}{t}\sum_{i=0}^{t-1} \text{pf}_i, \:t>0\]
    \item the portion of the buyers over all customers, expect for the new one,
        denoted by p (initialized to 0), which is computed by
        \[\text{p}_t=\frac{1}{t}\sum_{i=0}^{t-1} r_i, \:t>0\]
    \item the variance of the portion of buyers in their categories, denoted 
        by var: we divide customers (expect for the new one at current time 
        step) into 4 categories, according to their features, and for each 
        category, we compute the portion of the customers who buy our product,
        denoted by \(\text{pt}_i\) with \(i=1, 2, 3, 4\), then we compute the 
        variance of the 4 portions:
        \[\text{var}=\text{Var}(\text{pt})=\frac{\sum_{i=1}^{4} 
        \left(\text{pt}_i-\bar{\text{pt}}\right)^2}{3}\]
        Later we use this to compute reward to 
        make sure the agent will promote to all types of customers instead of 
        only focusing on one type.
        \vspace{2mm}\newline Note that \(\text{var}\leq1\).
\end{itemize}
In the end, the state \(s\), or \(s_t\) is of the form 
\(s_t=(x_t[0],\:\dots,\:x_t[14],\:\text{avg\_pf}_t,\:\text{p}_t,
\:\text{var}_t)\)

\subsection{Reward}
The reward at each time step \(t\), after the price \(c_t\) is promoted to the 
customer \(x_t\), denoted by \(R_t\), is calculated by
\[R_t = \text{pf}_t\left(1-h(\text{var}_t)\right)\]
where \(h\) is a function that indicates how much we care about the variance,
i.e. how important it is to try to promote to customers of all categories. In
this project I choose \(h\) to be such that 
\(h(\text{var}) = \sqrt{\text{var}}/2\).

\section{Build the model}
With the environment well built, we now build the model for our policy and the
value function. In this project we use artificial neuro networks (ANNs) as the 
parameterized policy and value function, each with four linear layers, and 
with the ReLU function as the activation function. And the input of both 
function is the state, as illustrated below:
\[S_t\rightarrow\underset{\text{ANN for value function}}{
        \boxed{
            \underset{len(S)\rightarrow 128}{\text{Linear}}
            \rightarrow\text{ReLU}
            \rightarrow\underset{128\rightarrow 256}{\text{Linear}}
            \rightarrow\text{ReLU}
            \rightarrow\underset{256\rightarrow 128}{\text{Linear}}
            \rightarrow\text{ReLU}
            \rightarrow\underset{128\rightarrow 1}{\text{Linear}}
        }
}\rightarrow v_t\]
\[S_t\rightarrow\underset{\text{ANN for policy function}}{
        \boxed{
            \underset{len(S)\rightarrow 128}{\text{Linear}}
            \rightarrow\text{ReLU}
            \rightarrow\underset{128\rightarrow 256}{\text{Linear}}
            \rightarrow\text{ReLU}
            \rightarrow\underset{256\rightarrow 512}{\text{Linear}}
            \rightarrow\text{ReLU}
            \rightarrow\underset{128\rightarrow n(A)}{\text{Linear}}
        }
}\rightarrow \text{Softmax}\rightarrow c_t\]
where \(len(S)\) denotes the vector length of the state and \(n(A)\) denotes the number of actions.

\section{RL with Actor-Critic}
In this project, we consider the episodic learning procedure, where each 
episode has finite time steps, \(N\), to be specified as a constant, and we 
will also reset the environment at the start of each episode. The algorithm 
below is to use RL, with actor-critic method, and with the help of what we 
have built in previous sections, to solve the problem:
\begin{algorithm}[H]
\caption{RL-Actor-Critic-for-financial-problem}
\begin{algorithmic}[1]
\State Initialize ANN policy parameterization 
\(\pi\left(c\middle|s, \bm{\theta}\right)\), with any \(\bm{\theta}\)
\State Initialize ANN state-value function parameterization
\(\hat{v}(s,\bm{w})\) with any \(\bm{w}\).
\State Step sizes \(\alpha_{\bm{\theta}}>0\), \(\alpha_{\bm{w}}>0\)
\Loop \hspace{0.3mm} (for each episode)
    \State Reset the environment
    \State Generate an \(x\) (first customer of the episode)
    \State Initialize \(S\) (first state of the episode)
    \State \(I \gets 1\)
    \Loop \hspace{0.3mm} (for each time step, \(N\) in total)
        \State \(c\sim\pi\left(\cdot\middle|S, \bm{\theta}\right)\)
        \State Take action \(c\), observe \(S'\), \(R\) from environment
        \State \(\delta \gets R + \gamma\hat{v}(S',\bm{w})-\hat{v}(S,\bm{w})\)
        \State \(\bm{w} \gets \bm{w} + 
        \alpha_{\bm{w}} \delta\nabla\hat{v}(S,\bm{w})\)
        \State \(\bm{\theta} \gets \bm{\theta} + \alpha_{\bm{\theta}}I\delta
        \nabla\ln{\pi\left(A\middle|S, \bm{\theta}\right)}\)
        \State \(I \gets \gamma I\)
        \State \(S \gets S'\)
    \EndLoop
\EndLoop
\end{algorithmic}
\end{algorithm}
\noindent The following graph illustrates the algorithm:
\vspace{5mm}
\begin{center}
    \begin{tikzpicture}[node distance=2cm]
        \node (agent) [process, minimum width=6cm, minimum height=3cm,
            label={[anchor=north east,inner sep=7pt]north east:Agent}]{};
        \node (pi) [process, left of=agent, xshift=0.5cm, yshift=-0.3cm] 
            {\(\pi\left(c\middle|s,\bm{\theta}\right)\)};
        \node (v) [process, right of=pi, xshift=1cm] 
            {\(\hat{v}\left(s,\bm{w}\right)\)};
        \node (env) [process, below of=pi, yshift=-2.5cm] {Environment};

        \draw [arrow] (pi) -- node[anchor=east] {c} (env);
        \draw [arrow] (env) 
            -- ++(0,-2.3) node[anchor=east, yshift=0.8cm] {\(S_{t+1}\)}
            -- ++(-1.5,0) coordinate(next_s);
        \draw [arrow] (next_s) -- ++(-1,0) -- ++ (0,10) -- ++(4,0) 
            -- ++(0,-1.7) 
            node[anchor=east, yshift=0.9cm] {\(S_t\)} coordinate(m1)
            -- (pi.93);
        \draw [arrow] (m1) -- (v.93);
        \draw [arrow] (env) 
            -- ++(3,0) coordinate(m2) node[anchor=south, xshift=-1cm] {\(R_t\)} 
            -- +(1.7,0) 
            node[anchor=south, xshift=-0.8cm] {\(\delta\)} coordinate(m3);
        \draw [arrow] (v) -- (m2) node[anchor=west, yshift=1.7cm] {\(v\)};
        \draw [dashed,arrow] (m3) -- ++(0,2.2) coordinate(m4) -- (pi.327);
        \draw [dashed,arrow] (m4) -- (v);
        \draw [dashed, thick] (-3,-6.5) -- (-3,-7.8);
    \end{tikzpicture}
\end{center}

\end{document}

### 2022-07-12 generate_data.py
remove unnecessary code

@@ -140,9 +140,3 @@ def generate_dataframe(constant_c=None, data_size=1000, without_response=False, 
 
 # generate data to fit glm
 # generate_dataframe(save=True, path='./data/dataframe_fit.csv', seed=0)
-
-# generate data to train
-# generate_dataframe(save=True, path='./data/dataframe_train.csv', without_response=True, seed=10)
-
-# generate data to test
-# generate_dataframe(save=True, path='./data/dataframe_test.csv', without_response=True, seed=20)

### 2022-07-13 a2c.py
plot the moving average reward by default

@@ -61,8 +61,8 @@ def a2c(environment):
 
     learning_rate = 3e-2
     gamma = 0.99
-    num_steps = 100
-    max_episodes = 2000
+    num_steps = 300
+    max_episodes = 3000
     num_state_features = 18
     price_low = 400
     price_high = 2700
@@ -77,14 +77,25 @@ def a2c(environment):
     actor_critic = actor_critic.to(device)
     actor_critic.train()
 
+    moving_avg_reward = 0
+
+    # plot settings:
     plt.ion()
+    fig, ax = plt.subplots()
+    ax.set_title("moving average reward with a2c")
+    ax.set_xlabel('episode')
+    ax.set_ylabel('moving average reward')
+    (line, ) = ax.plot([], [])
+    moving_avg_reward_pool = []
+    episode_pool = []
+    moving_avg_reward_pool_lim = None
+    ax.set(xlim=(0, 1))
 
     for episode in range(max_episodes):
         state = torch.from_numpy(environment.reset()).to(device)
         I = 1
-        total_reward = 0
 
-        for steps in range(num_steps):
+        for step in range(num_steps):
             value, policy_distro = actor_critic.forward(state)
             value, policy_distro = value.to(device)[0], policy_distro.to(device)
 
@@ -109,12 +120,29 @@ def a2c(environment):
 
             I = I * gamma
             state = new_state
-            total_reward += reward
+            moving_avg_reward += (reward - moving_avg_reward)/(episode * num_steps + step + 1)
 
         if episode % 5 == 0:
-            sys.stdout.write("Episode: {}, avg_reward: {}\n".format(episode, total_reward/num_steps))
-            plt.plot(episode, total_reward/num_steps, 'o')
-            plt.pause(0.25)
+            sys.stdout.write("Episode: {}, moving average reward: {}\n".format(episode, moving_avg_reward))
+
+            # update plot settings
+            if moving_avg_reward_pool_lim is None:
+                moving_avg_reward_pool_lim = [moving_avg_reward, moving_avg_reward]
+            elif moving_avg_reward > moving_avg_reward_pool_lim[1]:
+                moving_avg_reward_pool_lim[1] = moving_avg_reward
+            elif moving_avg_reward < moving_avg_reward_pool_lim[0]:
+                moving_avg_reward_pool_lim[0] = moving_avg_reward
+            ax.set(xlim=(-5, episode + 5),
[…]

### 2022-07-13 a2c.py
refactor

@@ -1,57 +1,10 @@
 import torch
 import sys
-import numpy as np
-import torch.nn as nn
 import torch.optim as optim
-from torch.autograd import Variable
 import statsmodels.api as sm
 import env
 import matplotlib.pyplot as plt
-
-
-class LogLayer(nn.Module):
-    def __init__(self):
-        super(LogLayer, self).__init__()
-
-    def forward(self, t):
-        return torch.log(t+torch.abs(torch.min(t)).detach()+1)
-
-
-# a2c network
-class ActorCritic(nn.Module):
-    def __init__(self, num_state_features, num_actions):
-        super(ActorCritic, self).__init__()
-        self.num_actions = num_actions
-
-        # value
-        self.critic_net = nn.Sequential(
-            nn.Linear(num_state_features, 64),
-            nn.ReLU(),
-            nn.Linear(64, 128),
-            nn.ReLU(),
-            nn.Linear(128, 1),
-        )
-
-        # policy
-        self.actor_net = nn.Sequential(
-            nn.Linear(num_state_features, 128),
-            nn.ReLU(),
-            nn.Linear(128, 256),
-            nn.ReLU(),
-            nn.Linear(256, 128),
-            nn.ReLU(),
-            nn.Linear(128, num_actions),
-            LogLayer(),     # to make numbers not differ too much
-            nn.Softmax(dim=0)
-        )
-
-    def forward(self, state):
-        state = Variable(state.float())
-
-        value = self.critic_net(state)
-        policy_distro = self.actor_net(state)
-
-        return value, policy_distro
+from model_utils import ActorCritic
 
 
 # train method
@@ -67,7 +20,7 @@ def a2c(environment):
     price_low = 400
     price_high = 2700
     price_step = 20
-    num_actions = int((price_high - price_low)/price_step)
+    num_actions = int((price_high - price_low) / price_step)
 
     device = torch.device('cuda:0' if torch.cuda.is_available() else 'cpu')
 
@@ -85,7 +38,7 @@ def a2c(environment):
     ax.set_title("moving average reward with a2c")
     ax.set_xlabel('episode')
     ax.set_ylabel('moving average reward')
-    (line, ) = ax.plot([], [])
+    (line,) = ax.plot([], [])
     moving_avg_reward_pool = []
     episode_pool = []
     moving_avg_reward_pool_lim = None
@@ -120,7 +73,7 @@ def a2c(environment):
 
             I = I * gamma
             state = new_state
[…]

### 2022-07-13 model_utils.py
initial commit

@@ -1,0 +1,53 @@
+import torch
+import torch.nn as nn
+from torch.autograd import Variable
+
+
+class LogLayer(nn.Module):
+    # k > 0, which is used to make sure the number we take log on is greater than 0
+    def __init__(self, k):
+        super(LogLayer, self).__init__()
+        self.k = k
+
+    def forward(self, t):
+        return torch.log(t + torch.abs(torch.min(t)).detach() + self.k)
+
+
+# a2c network
+class ActorCritic(nn.Module):
+    def __init__(self, num_state_features, num_actions):
+        super(ActorCritic, self).__init__()
+        self.num_actions = num_actions
+
+        # value
+        self.critic_net = nn.Sequential(
+            nn.Linear(num_state_features, 64),
+            nn.ReLU(),
+            nn.Linear(64, 128),
+            nn.ReLU(),
+            nn.Linear(128, 64),
+            nn.ReLU(),
+            nn.Linear(64, 1)
+        )
+
+        # policy
+        self.actor_net = nn.Sequential(
+            nn.Linear(num_state_features, 128),
+            nn.ReLU(),
+            nn.Linear(128, 256),
+            nn.ReLU(),
+            nn.Linear(256, 128),
+            nn.ReLU(),
+            nn.Linear(128, num_actions),
+            # take log to make numbers not differ too much with each other
+            LogLayer(1),
+            nn.Softmax(dim=0)
+        )
+
+    def forward(self, state):
+        state = Variable(state.float())
+
+        value = self.critic_net(state)
+        policy_distro = self.actor_net(state)
+
+        return value, policy_distro

### 2022-07-13 report/rl_qf_report.tex
modify policy model

@@
 finding an optimal policy is called policy iteration.
+
 \subsection{Value Iteration}
@@
         \boxed{
-            \underset{len(S)\rightarrow 128}{\text{Linear}}
+            \underset{n(S)\rightarrow 64}{\text{Linear}}
             \rightarrow\text{ReLU}
-            \rightarrow\underset{128\rightarrow 256}{\text{Linear}}
+            \rightarrow\underset{64\rightarrow 128}{\text{Linear}}
             \rightarrow\text{ReLU}
-            \rightarrow\underset{256\rightarrow 128}{\text{Linear}}
+            \rightarrow\underset{128\rightarrow 64}{\text{Linear}}
             \rightarrow\text{ReLU}
-            \rightarrow\underset{128\rightarrow 1}{\text{Linear}}
+            \rightarrow\underset{64\rightarrow 1}{\text{Linear}}
         }
@@
         \boxed{
-            \underset{len(S)\rightarrow 128}{\text{Linear}}
+            \underset{n(S)\rightarrow 128}{\text{Linear}}
             \rightarrow\text{ReLU}
@@
         }
-}\rightarrow \text{Softmax}\rightarrow c_t\]
-where \(len(S)\) denotes the vector length of the state and \(n(A)\) denotes the number of actions.
+}\rightarrow \text{Log} \rightarrow \text{Softmax}\rightarrow c_t\]
+where \(n(S)\) denotes the vector length of the state and \(n(A)\) denotes 
+the number of actions. 
+\vspace{3mm}\newline Note that we add a log layer before the Softmax layer 
+when getting the price, which takes the log of all entries of the input vector.
+This shrinks the difference between those entries, so that the output of 
+Softmax layer would be flatter, which means we will have a flatter policy 
+distribution, which is beneficial for training since it increase the 
+exploration for different actions.
 

### 2022-07-15 a2c.py
refactor

@@ -46,7 +46,6 @@ def a2c(environment):
 
     for episode in range(max_episodes):
         state = torch.from_numpy(environment.reset()).to(device)
-        I = 1
 
         for step in range(num_steps):
             value, policy_distro = actor_critic.forward(state)
@@ -64,14 +63,13 @@ def a2c(environment):
 
             advantage = (reward + gamma * value_next - value).detach()
             critic_loss = - advantage * value
-            actor_loss = - I * advantage * log_prob
+            actor_loss = - (gamma ** num_steps) * advantage * log_prob
             ac_loss = actor_loss + critic_loss
 
             ac_optimizer.zero_grad()
             ac_loss.backward()
             ac_optimizer.step()
 
-            I = I * gamma
             state = new_state
             moving_avg_reward += (reward - moving_avg_reward) / (episode * num_steps + step + 1)
 

### 2022-07-15 a2c.py
add a categorical customer feature

@@ -16,7 +16,7 @@ def a2c(environment):
     gamma = 0.99
     num_steps = 300
     max_episodes = 3000
-    num_state_features = 18
+    num_state_features = 21
     price_low = 400
     price_high = 2700
     price_step = 20
@@ -45,7 +45,10 @@ def a2c(environment):
     ax.set(xlim=(0, 1))
 
     for episode in range(max_episodes):
-        state = torch.from_numpy(environment.reset()).to(device)
+        state = torch.from_numpy(environment.reset())
+        state = torch.cat(
+            (state[:-1], torch.tensor([state[-1] == 0, state[-1] == 1, state[-1] == 2], dtype=torch.float))
+        ).to(device)
 
         for step in range(num_steps):
             value, policy_distro = actor_critic.forward(state)
@@ -57,7 +60,11 @@ def a2c(environment):
 
             # compute reward, go to next state to compute v'
             reward, new_state = environment.step(c.numpy())
-            new_state = torch.from_numpy(new_state).to(device)
+            new_state = torch.from_numpy(new_state)
+            new_state = torch.cat(
+                (new_state[:-1],
+                 torch.tensor([new_state[-1] == 0, new_state[-1] == 1, new_state[-1] == 2], dtype=torch.float))
+            ).to(device)
             value_next, _ = actor_critic.forward(new_state)
             value_next = value_next.to(device)[0]
 

### 2022-07-15 env.py

@@ -14,6 +14,8 @@ class Env:
         cols = ['gender', 'age', 'car_cost', 'miles', 'brand']
         for i in range(10):
             cols.append(f'rand_feature_{i}')
+        cols.append('level')
+
         cols.append('price')
         cols.append('response')
         cols.append('profit')

### 2022-07-15 generate_data.py

@@ -3,7 +3,7 @@ import pandas as pd
 from scipy import stats
 
 
-feature_size = 15
+feature_size = 16
 
 
 def generate_customer():
@@ -38,6 +38,9 @@ def generate_customer():
     customer[12] = np.random.normal(1.5, 5, 1)
     customer[13] = np.random.normal(1, 2, 1)
     customer[14] = np.random.normal(2, 4, 1)
+
+    # level: 0 -> poor, 1 -> medium, 2 -> rich
+    customer[15] = np.random.choice(3, 1)[0]
 
     return customer
 
@@ -85,6 +88,9 @@ def generate_raw_data(constant_c=None, data_size=1000, without_response=False, s
     for i in range(10):
         cols.append(f'rand_feature_{i}')
 
+    feature_data[15] = np.random.choice(3, data_size)
+    cols.append('level')
+
     feature_data = np.transpose(feature_data)
 
     # price
@@ -102,7 +108,8 @@ def generate_raw_data(constant_c=None, data_size=1000, without_response=False, s
         for i in range(data_size):
             t = age_mean/feature_data[i][1] + 1.2*miles_mean/feature_data[i][3] - 4*car_cost_mean/feature_data[i][2] \
                 - 2*10*.7/(feature_data[i][5]+1) - (feature_data[i][6] - 49)/50 + 1.5*feature_data[i][10] \
-                + 0.5*feature_data[i][11] - 2*feature_data[i][12] - 1.5*feature_data[i][13] + 2.5*price_mean/price[i]
+                + 0.5*feature_data[i][11] - 2*feature_data[i][12] - 1.5*feature_data[i][13] \
+                + (feature_data[i][15] + 1)*price_mean/price[i]
             # 50% normal(0, 1) and 60% t
             if abs(feature_data[i][7]) < 0.67 and abs(feature_data[i][9]) < 0.92:
                 if t > 0:
@@ -128,6 +135,7 @@ def generate_raw_data(constant_c=None, data_size=1000, without_response=False, s
     return data, cols
 
 
+# generate dataframe to fit glm
 def generate_dataframe(constant_c=None, data_size=1000, without_response=False, save=False,
                        path='./data/dataframe.csv', seed=0):
     raw_data, columns = generate_raw_data(constant_c=constant_c, data_size=data_size,

### 2022-07-15 report/rl_qf_report.tex
update policy gradient theorem with discounting
update feature number and fix typos

@@
 {\pi\left(A_t\middle|S_t, \bm{\theta}\right)}\right]\]
+And the discounted version of above is:
+\[\nabla J(\bm{\theta})\propto\mathbb{E}_\pi\left[
+        \gamma^{t}\Bigl(q_\pi(S_t,A_t)-b(S_t)\Big)
+        \frac{\nabla\pi\left(A_t\middle|S_t, \bm{\theta}\right)}
+{\pi\left(A_t\middle|S_t, \bm{\theta}\right)}\right]\]
 One natural choice for baseline is an estimate of the state value, 
@@
 The actor-critic method is based on the above updates formulas:
-\begin{algorithm}
+\begin{algorithm}[H]
 \caption{Actor-Critic}
@@
     \State Initialize \(S\) (first state of the episode)
-    \State \(I \gets 1\)
-    \Loop \hspace{0.3mm} (for each time step)
+    \Loop \hspace{0.3mm} (for each time step \(i\))
         \State \(A\sim\pi\left(\cdot\middle|S, \bm{\theta}\right)\)
@@
         \alpha_{\bm{w}} \delta\nabla\hat{v}(S,\bm{w})\)
-        \State \(\bm{\theta} \gets \bm{\theta} + \alpha_{\bm{\theta}}I\delta
+        \State \(\bm{\theta} \gets \bm{\theta} 
+        + \alpha_{\bm{\theta}}\gamma^{i}\delta
         \nabla\ln{\pi\left(A\middle|S, \bm{\theta}\right)}\)
-        \State \(I \gets \gamma I\)
         \State \(S \gets S'\)
@@
 A customer' features is represented by an array (or vector), denoted by \(x\) 
-with 15 entries with each generated randomly from a distribution, 
+with 16 entries with each generated randomly from a distribution, 
 including normal distribution, binomial distribution, and so on. For example, 
@@
     \begin{tabular}{c|c|c|c|c|c}
-        & customer feature 0 & \dots & customer feature 14 & price & resopnse\\
+        & customer feature 0 & \dots & customer feature 15 & price & resopnse\\
         \hline
-        1 & 1.0 & \dots & 3.278 & 1109.504 & 1.0\\
+        1 & 1.0 & \dots & 2.0 & 1109.504 & 1.0\\
         \hline
-        2 & 0.0 & \dots & 1.991 & 665.8 & 0.0\\
+        2 & 0.0 & \dots & 1.0 & 665.8 & 0.0\\
         \hline
@@
 The state at start of each time step is the feature vector of the new customer 
-to promote, appended by the portfolio, which is also a data vector consists of
-the following entries:
+to promote (might be modified a bit), appended by the portfolio, which is also 
+a data vector consists of the following entries:
 \begin{itemize}
@@
     \State Initialize \(S\) (first state of the episode)
-    \State \(I \gets 1\)
-    \Loop \hspace{0.3mm} (for each time step, \(N\) in total)
+    \Loop \hspace{0.3mm} (for each time step \(i\), \(N\) in total)
         \State \(c\sim\pi\left(\cdot\middle|S, \bm{\theta}\right)\)

### 2022-07-15 build_env.py
refactor

@@ -1,30 +1,0 @@
-import pandas as pd
-import statsmodels.api as sm
-import statsmodels.formula.api as smf
-
-
-def fit_glm(fit_df_path='./data/dataframe_fit.csv', save=False, path='./data/glm.model'):
-    df_fit = pd.read_csv(fit_df_path)
-    formula = 'response ~ gender'
-    for i in range(len(df_fit.columns) - 2):
-        formula += f' + {df_fit.columns[i + 1]}'
-
-    glm_raw = smf.glm(formula=formula, data=df_fit, family=sm.families.Binomial())
-    glm = glm_raw.fit()
-    if save:
-        glm.save(path)
-    # print(fitted_model.summary())
-    return glm
-
-
-def test_glm(glm_path='./data/glm.model', test_df_path='./data/dataframe_test.csv', index=0, num=10):
-    glm = sm.load(glm_path)
-    df_test = pd.read_csv(test_df_path)
-    instance = df_test.iloc[index:index + num]
-    pred = glm.predict(instance)
-    df_pred = pd.DataFrame(pred, columns=['pred'])
-    df_pred['true'] = instance['response']
-    print(df_pred)
-
-
-# fit_glm(save=True)

### 2022-07-15 data_utils.py

@@ -1,6 +1,8 @@
 import numpy as np
 import pandas as pd
 from scipy import stats
+import statsmodels.api as sm
+import statsmodels.formula.api as smf
 
 
 feature_size = 16
@@ -146,5 +148,29 @@ def generate_dataframe(constant_c=None, data_size=1000, without_response=False, 
     return df
 
 
-# generate data to fit glm
+def fit_glm(fit_df_path='./data/dataframe_fit.csv', save=False, path='./data/glm.model'):
+    df_fit = pd.read_csv(fit_df_path)
+    formula = 'response ~ gender'
+    for i in range(len(df_fit.columns) - 2):
+        formula += f' + {df_fit.columns[i + 1]}'
+
+    glm_raw = smf.glm(formula=formula, data=df_fit, family=sm.families.Binomial())
+    glm = glm_raw.fit()
+    if save:
+        glm.save(path)
+    # print(fitted_model.summary())
+    return glm
+
+
+def test_glm(glm_path='./data/glm.model', test_df_path='./data/dataframe_test.csv', index=0, num=10):
+    glm = sm.load(glm_path)
+    df_test = pd.read_csv(test_df_path)
+    instance = df_test.iloc[index:index + num]
+    pred = glm.predict(instance)
+    df_pred = pd.DataFrame(pred, columns=['pred'])
+    df_pred['true'] = instance['response']
+    print(df_pred)
+
+
 # generate_dataframe(save=True, path='./data/dataframe_fit.csv', seed=0)
+# fit_glm(save=True)

### 2022-07-15 env.py

@@ -1,6 +1,6 @@
 import pandas as pd
 import numpy as np
-import generate_data
+import data_utils
 
 
 class Env:
@@ -23,7 +23,7 @@ class Env:
         self.cols = cols
 
     def get_new(self):
-        self.current_customer = generate_data.generate_customer()
+        self.current_customer = data_utils.generate_customer()
         # groups:
         # car_cost\age    <40,    >=40
         # <70000          0       2

### 2022-07-15 policy_itr.py

@@ -1,131 +1,0 @@
-import numpy as np
-import sys
-import torch
-import torch.nn as nn
-import torch.optim as optim
-from torch.autograd import Variable
-import statsmodels.api as sm
-import env
-import matplotlib.pyplot as plt
-
-
-class LogLayer(nn.Module):
-    def __init__(self):
-        super(LogLayer, self).__init__()
-
-    def forward(self, t):
-        return torch.log(t+torch.abs(torch.min(t)).detach()+1)
-
-
-class Net(nn.Module):
-    def __init__(self, num_state_features, num_actions):
-        super(Net, self).__init__()
-        self.num_actions = num_actions
-
-        # value
-        self.value_net = nn.Sequential(
-            nn.Linear(num_state_features, 64),
-            nn.ReLU(),
-            nn.Linear(64, 128),
-            nn.ReLU(),
-            nn.Linear(128, 1)
-        )
-
-        # policy
-        self.policy_net = nn.Sequential(
-            nn.Linear(num_state_features, 128),
-            nn.ReLU(),
-            nn.Linear(128, 256),
-            nn.ReLU(),
-            nn.Linear(256, 128),
-            nn.ReLU(),
-            nn.Linear(128, num_actions),
-            LogLayer(),     # to make numbers not differ too much
-            nn.Softmax(dim=0)
-        )
-
-    def forward(self, state):
-        state = Variable(state.float())
-
-        value = self.value_net(state)
-        policy_distro = self.policy_net(state)
-
-        with torch.no_grad():
-            v = self.value_net(state)
-
-        return value, policy_distro, v
-
-
-# train method
-def policy_itr(environment):
-    # np.random.seed(123)
-    # torch.manual_seed(211)
-
-    learning_rate = 3e-2
-    gamma = 0.99
-    num_steps = 100
-    max_episodes = 2000
-    num_state_features = 18
-    price_low = 400
-    price_high = 2700
-    price_step = 20
-    num_actions = int((price_high - price_low)/price_step)
-
-    device = torch.device('cuda:0' if torch.cuda.is_available() else 'cpu')
-
-    net = Net(num_state_features, num_actions)
-    net_optimizer = optim.Adam(net.parameters(), lr=learning_rate)
-
-    net = net.to(device)
-    net.train()
-
-    plt.ion()
-
-    for episode in range(max_episodes):
-        state = torch.from_numpy(environment.reset()).to(device)
-        total_reward = 0
-
-        for steps in range(num_steps):
-            # policy evaluation
[…]

### 2022-07-16 model_utils.py
add reinforce model

@@ -17,7 +17,6 @@ class LogLayer(nn.Module):
 class ActorCritic(nn.Module):
     def __init__(self, num_state_features, num_actions):
         super(ActorCritic, self).__init__()
-        self.num_actions = num_actions
 
         # value
         self.critic_net = nn.Sequential(
@@ -51,3 +50,28 @@ class ActorCritic(nn.Module):
         policy_distro = self.actor_net(state)
 
         return value, policy_distro
+
+
+class Reinforce(nn.Module):
+    def __init__(self, num_state_features, num_actions):
+        super(Reinforce, self).__init__()
+
+        self.net = nn.Sequential(
+            nn.Linear(num_state_features, 128),
+            nn.ReLU(),
+            nn.Linear(128, 256),
+            nn.ReLU(),
+            nn.Linear(256, 128),
+            nn.ReLU(),
+            nn.Linear(128, num_actions),
+            # take log to make numbers not differ too much with each other
+            LogLayer(1),
+            nn.Softmax(dim=0)
+        )
+
+    def forward(self, state):
+        state = Variable(state.float())
+
+        policy_distro = self.net(state)
+
+        return policy_distro

### 2022-07-16 a2c.py
refactor

@@ -1,4 +1,5 @@
 import torch
+from torch.distributions import Categorical
 import sys
 import torch.optim as optim
 import statsmodels.api as sm
@@ -52,25 +53,24 @@ def a2c(environment):
 
         for step in range(num_steps):
             value, policy_distro = actor_critic.forward(state)
-            value, policy_distro = value.to(device)[0], policy_distro.to(device)
 
-            action = torch.multinomial(policy_distro.cpu(), 1, replacement=True)[0]
-            c = action * price_step + price_low
-            log_prob = torch.log(policy_distro[action])
+            distro = Categorical(policy_distro)
+            action = distro.sample()
+            c = action.item() * price_step + price_low
+            log_prob = distro.log_prob(action)
 
             # compute reward, go to next state to compute v'
-            reward, new_state = environment.step(c.numpy())
+            reward, new_state = environment.step(c)
             new_state = torch.from_numpy(new_state)
             new_state = torch.cat(
                 (new_state[:-1],
                  torch.tensor([new_state[-1] == 0, new_state[-1] == 1, new_state[-1] == 2], dtype=torch.float))
             ).to(device)
             value_next, _ = actor_critic.forward(new_state)
-            value_next = value_next.to(device)[0]
 
-            advantage = (reward + gamma * value_next - value).detach()
-            critic_loss = - advantage * value
-            actor_loss = - (gamma ** num_steps) * advantage * log_prob
+            advantage = (reward + gamma * value_next[0] - value[0]).detach()
+            critic_loss = - advantage * value[0]
+            actor_loss = - (gamma ** step) * advantage * log_prob
             ac_loss = actor_loss + critic_loss
 
             ac_optimizer.zero_grad()

### 2022-07-16 reinforce.py
Initial commit

@@ -1,0 +1,124 @@
+import torch
+import sys
+import torch.optim as optim
+import statsmodels.api as sm
+import env
+import matplotlib.pyplot as plt
+from model_utils import Reinforce
+from torch.distributions import Categorical
+
+
+# train method
+def reinforce(environment):
+    # np.random.seed(123)
+    # torch.manual_seed(211)
+
+    learning_rate = 1e-3
+    gamma = 0.99
+    num_steps = 300
+    max_episodes = 3000
+    num_state_features = 21
+    price_low = 400
+    price_high = 2700
+    price_step = 20
+    num_actions = int((price_high - price_low) / price_step)
+
+    device = torch.device('cuda:0' if torch.cuda.is_available() else 'cpu')
+
+    net = Reinforce(num_state_features, num_actions)
+    optimizer = optim.Adam(net.parameters(), lr=learning_rate)
+
+    net = net.to(device)
+    net.train()
+
+    moving_avg_reward = 0
+
+    # plot settings:
+    plt.ion()
+    fig, ax = plt.subplots()
+    ax.set_title("moving average reward with reinforce")
+    ax.set_xlabel('episode')
+    ax.set_ylabel('moving average reward')
+    (line,) = ax.plot([], [])
+    moving_avg_reward_pool = []
+    episode_pool = []
+    moving_avg_reward_pool_lim = None
+    ax.set(xlim=(0, 1))
+
+    for episode in range(max_episodes):
+        state = torch.from_numpy(environment.reset())
+        state = torch.cat(
+            (state[:-1], torch.tensor([state[-1] == 0, state[-1] == 1, state[-1] == 2], dtype=torch.float))
+        ).to(device)
+        log_prob_seq = []
+        reward_seq = []
+
+        # generate trajectory
+        for step in range(num_steps):
+            policy_distro = net.forward(state)
+
+            distro = Categorical(policy_distro)
+            action = distro.sample()
+            c = action.item() * price_step + price_low
+            log_prob_seq.append(torch.stack([distro.log_prob(action)]))
+
+            # compute reward, go to next state
+            reward, new_state = environment.step(c)
+            reward_seq.append(reward)
+            new_state = torch.from_numpy(new_state)
+            new_state = torch.cat(
+                (new_state[:-1],
+                 torch.tensor([new_state[-1] == 0, new_state[-1] == 1, new_state[-1] == 2], dtype=torch.float))
+            ).to(device)
+
+            state = new_state
+
[…]

### 2022-07-16 reinforce.py
update loss

@@ -13,9 +13,9 @@ def reinforce(environment):
     # np.random.seed(123)
     # torch.manual_seed(211)
 
-    learning_rate = 1e-3
+    learning_rate = 3e-3
     gamma = 0.99
-    num_steps = 300
+    num_steps = 200
     max_episodes = 3000
     num_state_features = 21
     price_low = 400
@@ -72,27 +72,25 @@ def reinforce(environment):
             ).to(device)
 
             state = new_state
-
             moving_avg_reward += (reward - moving_avg_reward) / (episode * num_steps + step + 1)
 
         # compute the return and loss
-        loss = []
+        losses = []
         returns = reward_seq.copy()
         for step in reversed(range(num_steps)):
             if step != num_steps - 1:
                 returns[step] += gamma * returns[step + 1]
-            loss.append(- (gamma ** step) * returns[step] * log_prob_seq[step])
+            losses.append(-(gamma ** step) * returns[step] * log_prob_seq[step])
 
         # update policy model parameters
-        for step in range(num_steps):
-            optimizer.zero_grad()
-            loss[step].backward()
-            optimizer.step()
-
-        # loss = torch.cat(loss).sum()
-        # optimizer.zero_grad()
-        # loss.backward()
-        # optimizer.step()
+        # for step in range(num_steps):
+        #     optimizer.zero_grad()
+        #     losses[step].backward()
+        #     optimizer.step()
+        loss = torch.cat(losses).sum()
+        optimizer.zero_grad()
+        loss.backward()
+        optimizer.step()
 
         if episode % 5 == 0:
             sys.stdout.write("Episode: {}, moving average reward: {}\n".format(episode, moving_avg_reward))

### 2022-07-17 reinforce.py
Update default learning rate

@@ -13,7 +13,7 @@ def reinforce(environment):
     # np.random.seed(123)
     # torch.manual_seed(211)
 
-    learning_rate = 3e-3
+    learning_rate = 3e-2
     gamma = 0.99
     num_steps = 200
     max_episodes = 3000

### 2022-07-18 ppo.py
Initial commit

@@ -1,0 +1,5 @@
+from model_utils import PPO
+
+
+def ppo(environment):
+    pass

### 2022-07-18 model_utils.py
Iadd PPO model

@@ -75,3 +75,12 @@ class Reinforce(nn.Module):
         policy_distro = self.net(state)
 
         return policy_distro
+
+
+class PPO(nn.Module):
+    def __init__(self, num_state_features, num_actions):
+        super(PPO, self).__init__()
+        self.net = None
+
+    def forward(self, state):
+        pass

### 2022-07-18 env.py
make compatible to latest pandas packages

@@ -48,11 +48,11 @@ class Env:
 
     def step(self, c):
         # promote price to customer
-        self.current_customer_df['price'] = c
+        self.current_customer_df['price'] = float(c)
 
         # glm generated response -> 1: buyer, 0: won't buy, and add this response to this customer's record
         pred = self.glm.predict(self.current_customer_df).gt(0.5).astype(int)[0]
-        self.current_customer_df['response'] = pred
+        self.current_customer_df['response'] = float(pred)
 
         # compute customer profit
         pf = pred * (c - self.g())
@@ -75,11 +75,11 @@ class Env:
     # compute expected reward and expected next state, but not step to it
     def peek_expected(self, c):
         # promote price to customer
-        self.current_customer_df['price'] = c
+        self.current_customer_df['price'] = float(c)
 
         # glm generated response -> 1: buyer, 0: won't buy, and add this response to this customer's record
         pred = self.glm.predict(self.current_customer_df).gt(0.5).astype(int)[0]
-        self.current_customer_df['response'] = pred
+        self.current_customer_df['response'] = float(pred)
 
         # compute customer profit
         pf = pred * (c - self.g())

### 2022-07-18 reinforce.py
update learning rate

@@ -13,7 +13,7 @@ def reinforce(environment):
     # np.random.seed(123)
     # torch.manual_seed(211)
 
-    learning_rate = 3e-2
+    learning_rate = 3e-5
     gamma = 0.99
     num_steps = 200
     max_episodes = 3000

### 2022-08-04 data_utils.py
refactor

@@ -131,10 +131,9 @@ def generate_dataframe(data_size, save=False, path='./data/dataframe.csv', seed=
 
 def fit_glm(fit_df_path='./data/dataframe_fit.csv', save=False, path='./data/glm.model'):
     df_fit = pd.read_csv(fit_df_path)
-    formula = 'response ~ gender'
-    for i in range(len(df_fit.columns) - 2):
-        formula += f' + {df_fit.columns[i + 1]}'
-
+    formula = 'response ~ gender + age + car_cost + miles + brand + rand_feature_0 + rand_feature_1 ' \
+              '+ rand_feature_2 + rand_feature_3 + rand_feature_4 + rand_feature_5 + rand_feature_6 ' \
+              '+ rand_feature_7 + rand_feature_8 + rand_feature_9 + level + price'
     glm_raw = smf.glm(formula=formula, data=df_fit, family=sm.families.Binomial())
     glm_fit = glm_raw.fit()
     if save:
@@ -142,8 +141,9 @@ def fit_glm(fit_df_path='./data/dataframe_fit.csv', save=False, path='./data/glm
     return glm_fit
 
 
-def plot_csv(models, indices):
-    dfs = [pd.read_csv('data/' + model + '_out.csv', header=None) for model in models]
+def plot_csv(models, indices, csv_paths=None):
+    dfs = [pd.read_csv('data/' + model + '_out.csv', header=None) for model in models] if not csv_paths \
+        else [pd.read_csv(csv_path) for csv_path in csv_paths]
     fig, axs = plt.subplots(len(models), figsize=(10, len(models) * 4))
     fig.supxlabel('Iteration')
     fig.supylabel('Moving Average Reward')

### 2022-08-04 a2c.py
add comments

@@ -7,17 +7,15 @@ import env
 from model_utils import Actor, Critic
 
 
-# train method
 def a2c(environment, hp):
+    moving_avg_reward_pool = []
+
     actor, critic = \
         Actor(hp.num_state_features, (hp.price_max - hp.price_min) / hp.price_binwidth), Critic(hp.num_state_features)
     actor_optimizer, critic_optimizer = \
         optim.Adam(actor.parameters(), lr=hp.actor_lr), optim.Adam(critic.parameters(), lr=hp.critic_lr)
 
     actor, critic = actor.to(hp.device), critic.to(hp.device)
-
-    moving_avg_reward_pool = []
-
     actor.train()
     critic.train()
     for i in range(hp.num_itr):
@@ -25,18 +23,24 @@ def a2c(environment, hp):
         price_mean = 0
         actor_loss_mean = 0
         critic_loss_mean = 0
+
+        # run a trajectory
         state = torch.from_numpy(environment.reset()).to(hp.device)
         for step in range(hp.episode_size):
+            # get policy distribution and value for current state, compute price and log probability
             policy_distro = actor.forward(state)
             action = policy_distro.sample()
             log_prob = policy_distro.log_prob(action)
             price = hp.price_min + action * hp.price_binwidth
             v = critic.forward(state)
 
+            # step to next state, get reward and value for next state, then compute advantage
             r, state = environment.step(price.item())
             state = torch.from_numpy(state).to(hp.device)
             v_next = critic.forward(state)
             advantage = (r + hp.gamma * v_next - v).detach()
+
+            # compute loss for actor and critic, update parameters accordingly
             actor_loss = - (hp.gamma ** step) * advantage * log_prob
             critic_loss = - advantage * v
             actor_loss_mean += actor_loss
@@ -45,7 +49,6 @@ def a2c(environment, hp):
             actor_optimizer.zero_grad()
             actor_loss.backward()
             actor_optimizer.step()
-
             critic_optimizer.zero_grad()
             critic_loss.backward()
             critic_optimizer.step()

### 2022-08-04 a2c.py
add comments

@@ -34,7 +34,7 @@ def a2c(environment, hp):
             price = hp.price_min + action * hp.price_binwidth
             v = critic.forward(state)
 
-            # step to next state, get reward and value for next state, then compute advantage
+            # get reward, step to next state and get value for next state, then compute advantage
             r, state = environment.step(price.item())
             state = torch.from_numpy(state).to(hp.device)
             v_next = critic.forward(state)

### 2022-08-04 ppo.py

@@ -9,15 +9,14 @@ from model_utils import Actor, Critic
 
 
 def ppo(environment, hp):
+    moving_avg_reward_pool = []
+
     actor, critic = \
         Actor(hp.num_state_features, (hp.price_max - hp.price_min) / hp.price_binwidth), Critic(hp.num_state_features)
     actor_optimizer, critic_optimizer = \
         optim.Adam(actor.parameters(), lr=hp.actor_lr), optim.Adam(critic.parameters(), lr=hp.critic_lr)
 
     actor, critic = actor.to(hp.device), critic.to(hp.device)
-
-    moving_avg_reward_pool = []
-
     actor.train()
     critic.train()
     for i in range(hp.num_itr):
@@ -33,13 +32,13 @@ def ppo(environment, hp):
             for _ in range(hp.episode_size):
                 batch_states.append(state)
 
-                # compute action by current policy
+                # get policy distribution for current state, compute action, price, and log probability
                 policy_distro = actor.forward(state)
                 action = policy_distro.sample()
                 log_prob = policy_distro.log_prob(action)
                 price = hp.price_min + action * hp.price_binwidth
 
-                # compute reward and go to next state
+                # get reward and step to next state
                 r, state = environment.step(price.item())
                 state = torch.from_numpy(state).to(hp.device)
 
@@ -60,6 +59,7 @@ def ppo(environment, hp):
         batch_returns = torch.flatten(torch.tensor(batch_returns, dtype=torch.float)).to(hp.device)
         values = critic(batch_states)
         advantages = (batch_returns - values.squeeze()).detach()
+        # normalize advantages
         advantages = (advantages - advantages.mean()) / (advantages.std() + 1e-10)
 
         # update network
@@ -77,7 +77,6 @@ def ppo(environment, hp):
             actor_optimizer.zero_grad()
             actor_loss.backward()
             actor_optimizer.step()
-
             critic_optimizer.zero_grad()
             critic_loss.backward()
             critic_optimizer.step()

### 2022-08-04 reinforce.py

@@ -8,13 +8,12 @@ from model_utils import Actor
 
 
 def reinforce(environment, hp):
+    moving_avg_reward_pool = []
+
     actor = Actor(hp.num_state_features, (hp.price_max - hp.price_min) / hp.price_binwidth)
     actor_optimizer = optim.Adam(actor.parameters(), lr=hp.actor_lr)
 
     actor = actor.to(hp.device)
-
-    moving_avg_reward_pool = []
-
     actor.train()
     for i in range(hp.num_itr):
         moving_avg_reward = 0
@@ -22,14 +21,17 @@ def reinforce(environment, hp):
         ep_actions = []
         ep_returns = []
         actor_loss_mean = 0
+
         # run a trajectory
         state = torch.from_numpy(environment.reset()).to(hp.device)
         for step in range(hp.episode_size):
+            # get policy distribution for current state, compute price
             ep_states.append(state)
             policy_distro = actor.forward(state)
             action = policy_distro.sample()
             price = hp.price_min + action * hp.price_binwidth
 
+            # get reward and step to next state
             r, state = environment.step(price.item())
             state = torch.from_numpy(state).to(hp.device)
 
@@ -41,6 +43,7 @@ def reinforce(environment, hp):
         for t in reversed(range(len(ep_returns) - 1)):
             ep_returns[t] += hp.gamma * ep_returns[t + 1]
         ep_returns = torch.tensor(ep_returns, dtype=torch.float)
+        # normalize returns
         ep_returns = (ep_returns - ep_returns.mean()) / (ep_returns.std(dim=0) + 1e-10)
 
         # update policy network

### 2022-08-04 env.py
add comments

@@ -6,22 +6,26 @@ import data_utils
 class Env:
     def __init__(self, glm):
         self.glm = glm
+        # dataframe that records all customers information so far, unless reset
         self.df = None
+        # current customer being promoted
         self.current_customer = None
+        # current state fed or to be fed to the network
         self.state = None
+        # current customer being promoted, of type pandas dataframe
         self.current_customer_df = None
 
         cols = ['gender', 'age', 'car_cost', 'miles', 'brand']
         for i in range(10):
             cols.append(f'rand_feature_{i}')
         cols.append('level')
-
         cols.append('price')
         cols.append('response')
         cols.append('profit')
         cols.append('group')
         self.cols = cols
 
+    # generate new customer
     def get_new(self):
         self.current_customer = data_utils.generate_customer()
         # groups:
@@ -34,17 +38,16 @@ class Env:
         self.current_customer_df = pd.DataFrame(data=customer, columns=self.cols)
 
     def reset(self):
+        self.df = pd.DataFrame(columns=self.cols)
         self.get_new()
         # append average_profit, portion, variance
         self.state = np.concatenate((self.current_customer[:-1], [self.current_customer[-1] == 0,
                                                                   self.current_customer[-1] == 0,
                                                                   self.current_customer[-1] == 0], [0, 0, 0]))
-        self.df = pd.DataFrame(columns=self.cols)
         return self.state
 
     def g(self):
         return 0
-        # return self.current_customer[2]/60
 
     def h(self, var):
         return np.sqrt(var)/2
@@ -78,7 +81,7 @@ class Env:
         return pf*(1 - self.h(var)), self.state
 
 
-# group buyers percentage, there are 4 groups
+# variance of group buyers percentage, there are 4 groups
 def count_var(df):
     p = np.zeros(4)
     group_p = df.groupby('group').mean()['response']

### 2022-08-04 model_utils.py

@@ -3,7 +3,6 @@ from torch.distributions import Categorical
 from torch.autograd import Variable
 
 
-# actor network
 class Actor(nn.Module):
     def __init__(self, in_dim, out_dim):
         super(Actor, self).__init__()
@@ -13,7 +12,7 @@ class Actor(nn.Module):
             nn.Linear(128, 128),
             nn.ReLU(),
             nn.Linear(128, int(out_dim)),
-            nn.Threshold(.1, .1),
+            nn.Threshold(.1, .1)
         )
 
     def forward(self, state):
@@ -22,7 +21,6 @@ class Actor(nn.Module):
         return policy_distro
 
 
-# critic network
 class Critic(nn.Module):
     def __init__(self, in_dim):
         super(Critic, self).__init__()

### 2022-08-05 a2c.py
refactor

@@ -92,3 +92,6 @@ def train_a2c():
     glm = sm.load('./data/glm.model')
     env_train = env.Env(glm)
     a2c(env_train, hyperparameter)
+
+
+# train_a2c()

### 2022-08-05 main.py

@@ -1,17 +1,12 @@
 from data_utils import generate_dataframe, fit_glm, plot_csv
-from a2c import train_a2c
-from reinforce import train_reinforce
-from ppo import train_ppo
 
 # generate data and use that to fit glm
 # df = generate_dataframe(data_size=10000, save=True, path='./data/dataframe_fit.csv', seed=0)
 # glm = fit_glm(save=True)
 # print(glm.summary())
 
-# train different models
-# train_a2c()
-# train_reinforce()
-# train_ppo()
-
 # plot the result
+# plot_csv(models=['a2c']*4, indices=range(4))
+# plot_csv(models=['reinforce']*4, indices=range(4))
+# plot_csv(models=['ppo']*4, indices=range(4))
 # plot_csv(models=['a2c', 'reinforce', 'ppo'], indices=[0, 0, 0])

### 2022-08-05 ppo.py

@@ -114,3 +114,6 @@ def train_ppo():
     glm = sm.load('./data/glm.model')
     env_train = env.Env(glm)
     ppo(env_train, hyperparameter)
+
+
+# train_ppo()

### 2022-08-05 reinforce.py

@@ -89,3 +89,6 @@ def train_reinforce():
     glm = sm.load('./data/glm.model')
     env_train = env.Env(glm)
     reinforce(env_train, hyperparameter)
+
+
+# train_reinforce()

### 2022-08-06 main.py
update

@@ -6,7 +6,7 @@ from data_utils import generate_dataframe, fit_glm, plot_csv
 # print(glm.summary())
 
 # plot the result
-# plot_csv(models=['a2c']*4, indices=range(4))
-# plot_csv(models=['reinforce']*4, indices=range(4))
-# plot_csv(models=['ppo']*4, indices=range(4))
-# plot_csv(models=['a2c', 'reinforce', 'ppo'], indices=[0, 0, 0])
+# plot_csv(models=['a2c']*6, indices=range(6))
+# plot_csv(models=['reinforce']*6, indices=range(6))
+# plot_csv(models=['ppo']*6, indices=range(6))
+# plot_csv(models=['a2c', 'reinforce', 'ppo'], indices=[5, 5, 5])

### 2022-08-07 report/rl_qf_report.tex
update model structure

@@
 value function. In this project we use artificial neuro networks (ANNs) as the 
-parameterized policy and value function, each with four linear layers, and 
+parameterized policy and value function, each with three linear layers, and 
 with the ReLU function as the activation function. And the input of both 
@@
         \boxed{
-            \underset{n(S)\rightarrow 64}{\text{Linear}}
+            \underset{n(S)\rightarrow 128}{\text{Linear}}
             \rightarrow\text{ReLU}
-            \rightarrow\underset{64\rightarrow 128}{\text{Linear}}
+            \rightarrow\underset{128\rightarrow 128}{\text{Linear}}
             \rightarrow\text{ReLU}
-            \rightarrow\underset{128\rightarrow 64}{\text{Linear}}
-            \rightarrow\text{ReLU}
-            \rightarrow\underset{64\rightarrow 1}{\text{Linear}}
+            \rightarrow\underset{128\rightarrow 1}{\text{Linear}}
         }
@@
             \rightarrow\text{ReLU}
-            \rightarrow\underset{128\rightarrow 256}{\text{Linear}}
-            \rightarrow\text{ReLU}
-            \rightarrow\underset{256\rightarrow 512}{\text{Linear}}
+            \rightarrow\underset{128\rightarrow 128}{\text{Linear}}
             \rightarrow\text{ReLU}
             \rightarrow\underset{128\rightarrow n(A)}{\text{Linear}}
+            \rightarrow\underset{(0.1, \: 0.1)}{\text{Threshold}}
         }
-}\rightarrow \text{Log} \rightarrow \text{Softmax}\rightarrow c_t\]
+}\rightarrow \pi_t\rightarrow c_t\]
 where \(n(S)\) denotes the vector length of the state and \(n(A)\) denotes 
 the number of actions. 
-\vspace{3mm}\newline Note that we add a log layer before the Softmax layer 
-when getting the price, which takes the log of all entries of the input vector.
-This shrinks the difference between those entries, so that the output of 
-Softmax layer would be flatter, which means we will have a flatter policy 
-distribution, which is beneficial for training since it increase the 
-exploration for different actions.
+\vspace{3mm}\newline We generate the policy distribution by scoring each 
+action. E.g. denoted the policy function output by \(y\), then the probability 
+of choosing action \(i\) (\(i=0, 1, ..., n(A) - 1\)) is computed by 
+\[P(i)=\frac{y_i}{\sum_{j=0}^{n(A)-1} y_j}\]
+Note that we add a Threshold layer at the end of policy 
+function, which is defined by 
+\[\text{Threshold}(0.1, 0.1)=\text{max}(0.1, x)\]
+which makes sure that 
+\begin{enumerate}
+    \item the probabilities are valid (no negative values, greater score 
+        results in greater probability);
+    \item all actions have the probability to be chosen at early stage, which 
+        is beneficial for training since it increase the exploration for 
+        different actions.
+\end{enumerate}
 

### 2022-08-07 data_utils.py
allow saving the graphs

@@ -141,7 +141,7 @@ def fit_glm(fit_df_path='./data/dataframe_fit.csv', save=False, path='./data/glm
     return glm_fit
 
 
-def plot_csv(models, indices, csv_paths=None):
+def plot_csv(models, indices, csv_paths=None, save_path=None):
     dfs = [pd.read_csv('data/' + model + '_out.csv', header=None) for model in models] if not csv_paths \
         else [pd.read_csv(csv_path) for csv_path in csv_paths]
     fig, axs = plt.subplots(len(models), figsize=(10, len(models) * 4))
@@ -149,8 +149,14 @@ def plot_csv(models, indices, csv_paths=None):
     fig.supylabel('Moving Average Reward')
     ys = [dfs[i].iloc[indices[i]] for i in range(len(models))]
     xs = [range(len(y)) for y in ys]
-    for i in range(len(axs)):
-        axs[i].set_title('Moving Average Reward with ' + models[i])
-        axs[i].plot(xs[i], ys[i])
+    if len(models) == 1:
+        axs.set_title('Moving Average Reward with ' + models[0])
+        axs.plot(xs[0], ys[0])
+    else:
+        for i in range(len(axs)):
+            axs[i].set_title('Moving Average Reward with ' + models[i])
+            axs[i].plot(xs[i], ys[i])
     plt.tight_layout()
+    if save_path is not None:
+        plt.savefig(save_path)
     plt.show()

### 2022-08-07 main.py
update

@@ -6,7 +6,7 @@ from data_utils import generate_dataframe, fit_glm, plot_csv
 # print(glm.summary())
 
 # plot the result
-# plot_csv(models=['a2c']*6, indices=range(6))
+# plot_csv(models=['a2c'], indices=[5], save_path='./data/a2c_out.png')
 # plot_csv(models=['reinforce']*6, indices=range(6))
 # plot_csv(models=['ppo']*6, indices=range(6))
-# plot_csv(models=['a2c', 'reinforce', 'ppo'], indices=[5, 5, 5])
+# plot_csv(models=['a2c', 'reinforce', 'ppo'], indices=[5, 5, 5], save_path='./data/out.png')

### 2022-08-07 report/rl_qf_report.tex
update training result, finish Reinforce algorithm, working on PPO algorithm

@@
 \usepackage{amsmath, amsfonts, bm, listings, enumitem, geometry, titlesec,
-array, makecell, caption, graphicx, float, algorithm, algpseudocode}
+array, makecell, caption, graphicx, float, algorithm, algpseudocode, siunitx}
 \usepackage[table]{xcolor}
@@
 \geometry{margin=0.8in}
-\graphicspath{ {./imgs/} }
+\graphicspath{ {../data/} }
+
 %\renewcommand{\familydefault}{\sfdefault}
-
+%\sisetup{output-exponent-marker=\ensuremath{\mathrm{e}}}
 \tikzstyle{process} = [rectangle, minimum width=2cm, minimum height=1.3cm, 
@@
 \section{RL with Actor-Critic}
+\subsection{The Algorithm}
 In this project, we consider the episodic learning procedure, where each 
-episode has finite time steps, \(N\), to be specified as a constant, and we 
+episode has finite time steps, \(T\), to be specified as a constant, and we 
 will also reset the environment at the start of each episode. The algorithm 
@@
 \begin{algorithm}[H]
-\caption{RL-Actor-Critic-for-financial-problem}
+\caption{Actor-Critic for our financial problem}
 \begin{algorithmic}[1]
@@
     \State Initialize \(S\) (first state of the episode)
-    \Loop \hspace{0.3mm} (for each time step \(i\), \(N\) in total)
+    \Loop \hspace{0.3mm} (for each time step \(t\), \(T\) in total)
         \State \(c\sim\pi\left(\cdot\middle|S, \bm{\theta}\right)\)
@@
         \State \(\bm{\theta} \gets \bm{\theta} 
-        + \alpha_{\bm{\theta}}\gamma^{i}\delta
+        + \alpha_{\bm{\theta}}\gamma^{t}\delta
         \nabla\ln{\pi\left(A\middle|S, \bm{\theta}\right)}\)
@@
 
+\subsection{Training Result}
+The following graph shows the training result of the above algorithm (300
+moving average reward vs iteration), with 600 iterations (5 episodes per 
+iteration), \(T=300\), \(\gamma=0.99\), 
+\(\alpha_\theta=\alpha_{\bm{w}}=\num{3e-4}\).
+\begin{center}
+    \includegraphics[scale=0.67]{a2c_out}
+\end{center}
+The graph shows that the moving average reward converges within only 50 
+iterations, that is, 250 episode, 75000 parameter updates for each network, 
+and stays quite stable afterwards.
+
+\section{Actor-Critic, Reinforce, and PPO}
+To further show how Actor-Critic algorithm performs, we compare it to another
+two popular algorithms: Reinforce and PPO. Below are pseudocodes for the two
+algorithms.
+\begin{algorithm}[H]
+\caption{Reinforce for our financial problem}
+\begin{algorithmic}[1]
+\State Initialize ANN policy parameterization 
+\(\pi\left(c\middle|s, \bm{\theta}\right)\), with any \(\bm{\theta}\)
+\State Step sizes \(\alpha_{\bm{\theta}}>0\)
+\Loop \hspace{0.3mm} (for each episode)
+    \State Reset the environment
+    \State Generate an episode \(S_0, A_0, R_1, ..., S_{T-1}, A_{T-1}, R_T\),
+    following \(\pi\left(\cdot\middle|\cdot, \bm{\theta}\right)\)
+    \Loop \hspace{0.3mm} (for each time step \(t\), \(T\) in total)
+        \State \(G \gets \sum_{k=t+1}^{T} \gamma^{k-t-1}R_k\)
+        \State \(\bm{\theta} \gets \bm{\theta} + \alpha_{\bm{\theta}}\gamma^t
+        G\nabla{\ln{\pi\left(A_t\middle|S_t, \bm{\theta}\right)}}\)
+    \EndLoop
+\EndLoop
+\end{algorithmic}
+\end{algorithm}
+
+\begin{algorithm}[H]
+\caption{PPO for our financial problem}
+\begin{algorithmic}[1]
+\State Initialize ANN policy parameterization 
+\(\pi\left(c\middle|s, \bm{\theta}\right)\), with any \(\bm{\theta}\)
+\State Initialize ANN state-value function parameterization
+\(\hat{v}(s,\bm{w})\) with any \(\bm{w}\).
+\State Step sizes \(\alpha_{\bm{\theta}}>0\), \(\alpha_{\bm{w}}>0\)
+\For{\(k=0, 1, 2, ...\)}
+    \State Collect set of trajectories \(\mathcal{D}_k=\{\tau_i\}\), 
+    following \(\pi\left(c\middle|s, \bm{\theta}\right)\)
+    \State Compute discounted returns \(G_k\), the same way as in Reinforce
+    algorithm
+\EndFor
+\end{algorithmic}
+\end{algorithm}
+
 \end{document}

### 2022-08-07 report/rl_qf_report.tex
update PPO algorithm

@@
     \State Initialize \(S\) (first state of the episode)
-    \Loop \hspace{0.3mm} (for each time step \(t\), \(T\) in total)
+    \For{\(t=0, 1, ..., T\)}
         \State \(c\sim\pi\left(\cdot\middle|S, \bm{\theta}\right)\)
@@
         \State \(S \gets S'\)
-    \EndLoop
+    \EndFor
 \EndLoop
@@
 two popular algorithms: Reinforce and PPO. Below are pseudocodes for the two
-algorithms.
+algorithms:
 \begin{algorithm}[H]
@@
     \State Reset the environment
-    \State Generate an episode \(S_0, A_0, R_1, ..., S_{T-1}, A_{T-1}, R_T\),
+    \State Generate an episode \(S_0, C_0, R_1, ..., S_{T-1}, C_{T-1}, R_T\),
     following \(\pi\left(\cdot\middle|\cdot, \bm{\theta}\right)\)
-    \Loop \hspace{0.3mm} (for each time step \(t\), \(T\) in total)
+    \For{\(t=0, 1, ..., T\)}
         \State \(G \gets \sum_{k=t+1}^{T} \gamma^{k-t-1}R_k\)
         \State \(\bm{\theta} \gets \bm{\theta} + \alpha_{\bm{\theta}}\gamma^t
-        G\nabla{\ln{\pi\left(A_t\middle|S_t, \bm{\theta}\right)}}\)
-    \EndLoop
+        G\nabla{\ln{\pi\left(C_t\middle|S_t, \bm{\theta}\right)}}\)
+    \EndFor
 \EndLoop
@@
 \State Step sizes \(\alpha_{\bm{\theta}}>0\), \(\alpha_{\bm{w}}>0\)
-\For{\(k=0, 1, 2, ...\)}
+\For{iteration \(k=0, 1, 2, ...\)}
     \State Collect set of trajectories \(\mathcal{D}_k=\{\tau_i\}\), 
-    following \(\pi\left(c\middle|s, \bm{\theta}\right)\)
-    \State Compute discounted returns \(G_k\), the same way as in Reinforce
-    algorithm
+    following \(\pi\left(\cdot\middle|\cdot, \bm{\theta}_k\right)\), where 
+    \(\tau = S_0, C_0, R_1, ..., S_{T-1}, C_{T-1}, R_T\)
+    \For{\(t=0, 1, ..., T\) in each trajectory \(\tau\) in \(\mathcal{D}_k\)}
+        \State \(G_t \gets \sum_{k=t+1}^{T} \gamma^{k-t-1}R_k\)
+        \State \(A_t \gets G_t - \hat{v}(S_t)\)
+    \EndFor
+    \Loop \hspace{0.3mm} (update multiple times)
+    \State \(\bm{\theta} \gets \underset{\bm{\theta}}{\text{arg\:max}}
+    \frac{1}{|\mathcal{D}_k|T}\sum_{\tau\in\mathcal{D}_k}^{} \sum_{t=0}^{T} 
+    \min{\left(
+            \frac{\pi\left(c_t\middle|S_t, \bm{\theta}\right)}
+            {\pi\left(c_t\middle|S_t, \bm{\theta}_k\right)}A_t, g(\epsilon, A_t)
+    \right)}\)
+    \State \(\bm{w} \gets \underset{\bm{w}}{\text{arg\:min}}
+    \frac{1}{|\mathcal{D}_k|T}\sum_{\tau\in\mathcal{D}_k}^{} \sum_{t=0}^{T} 
+    \Bigl(\hat{v}(S_t, \bm{w})-G_t\Bigr)^2\)
+    \EndLoop
 \EndFor

### 2022-08-08 report/rl_qf_report.tex
make comparison for three algorithms

@@
 \section{Actor-Critic, Reinforce, and PPO}
+\subsection{Algorithms}
 To further show how Actor-Critic algorithm performs, we compare it to another
@@
             \frac{\pi\left(c_t\middle|S_t, \bm{\theta}\right)}
-            {\pi\left(c_t\middle|S_t, \bm{\theta}_k\right)}A_t, g(\epsilon, A_t)
+            {\pi\left(c_t\middle|S_t, \bm{\theta}_k\right)}A_t,
+            \text{clip}\left(
+                \frac{\pi\left(c_t\middle|S_t, \bm{\theta}\right)}
+                {\pi\left(c_t\middle|S_t, \bm{\theta}_k\right)},
+                1-\epsilon, 1+\epsilon
+            \right)A_t
     \right)}\)
@@
 
+\subsection{Training result}
+To make better comparison, the policy function of the two algorithms
+is implemented the same way as we did in Actor-Critic algorithm, and the same 
+is true for the value function used in PPO method. 
+\vspace{3mm}\newline The following graph shows the training result of these 
+three algorithms (300 moving average reward vs iteration), with 600 iterations
+(5 episodes per iteration), \(T=300\), \(\gamma=0.99\), 
+\(\alpha_\theta=\num{3e-4}\), \(\alpha_{\bm{w}}=\num{3e-10}\) (if applicable),
+\(\epsilon=0.5\) (if applicable).
+\begin{center}
+    \includegraphics[scale=0.67]{out}
+\end{center}
+As is shown in the graph, the Actor-Critic algorithm converges the fastest,
+within 50 iterations, followed by Reinforce algorithm, which converges within
+about 250 iterations, despite a small drop of moving average around iteration 
+300, which is quickly corrected by the algorithm within 50 iterations. PPO 
+algorithm converges the slowest, with about 300 iterations. Despite of the 
+speed of convergence, the moving average rewards of convergence for these 
+three algorithms are nearly the same (around 400), this is as expected.
+
 \end{document}

### 2022-08-17 papers/paper_2-col.tex
write up paper for this research

--- 2022-08-08 report/rl_qf_report.tex
@@
-\documentclass[11pt]{article}
-\usepackage{amsmath, amsfonts, bm, listings, enumitem, geometry, titlesec,
-array, makecell, caption, graphicx, float, algorithm, algpseudocode, siunitx}
-\usepackage[table]{xcolor}
+% !TEX encoding = UTF-8 Unicode
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
+%%
+%%  This file is asmeconf-template.tex, a LaTeX template to format ASME Conference papers according to
+%%  the requirements on ASME's conference web pages, and including hypertext support for the pdf.
+%%
+%%  This file is version 1.31 dated 2022/07/04
+%%  
+%%  As of version 1.11, this template defaults to ASME's newer conference guidelines first posted July 2019.
+%% 			Those guidelines changed the requested author block formatting to be inline. 
+%%			This LaTeX template continues to support the traditional grid format as a package option, [grid].
+%%			Nomenclature now follows the abstract. Abstract text is set in italics.
+%%
+%%  Author: John H. Lienhard V
+%%          Department of Mechanical Engineering
+%%          Massachusetts Institute of Technology
+%%          Cambridge, MA 02139-4307 USA
+%%
+%%  Class options include:
+%%
+%%          * Math options from M. Sharpe's newtxmath package: upright integrals [upint]; 
+%%          *    [varvw] for a v and w that are better distinguished from Greek nu; and also 
+%%          *    [subscriptcorrection, smallerops, varg, frenchmath, varbb, cmbraces, slantedGreek,...] 
+%%			* 	 See newtx documentation for descriptions (at CTAN: http://ctan.org, v1.6 or higher is best).
+%%
+%%          * Options to: 	omit the ASME copyright footer [nofoot]; 
+%%			*				use government employee copyright notice [govt];
+%%			*				use government contractor copyright notice [contractor]
+%%
+%%          * An option to use the traditional grid arrangement of author names [grid].  
+%%			*	 With this option, line breaks (\\) may be inserted into the address as needed. 
+%%			*	 Author names that include commas should be enclosed in braces, e.g., {Joseph L. Smith, Jr.}.  
+%%			*	 Authors may be grouped above a single affiliation using braces, e.g., {Henry Tudor, Catherine Parr}.
+%%
+%%          * An option to balance the heights of columns on the last page [balance]. 
+%%          *    This option is NOT compatible with the [lineno] option.
+%%
+%%          * An option to include line numbers [lineno]. You must *run twice* for proper placement of the line numbers. 
+%%			*	 The lineno package does not number titles, footnotes, captions, or tables.
+%%          *    This option will disable balancing column height on final page if that option has been invoked.
+%%          *    The lineno package won't always number the lines preceding displayed math in a paragraph because
+%%          *    paragraph has not ended.  See that package's documentation for macros to address this problem, or
+%%          *    just leave a blank line above the displayed equation while you are editing and then remove the 
+%%          *    blank line and [lineno] option when you move to your final version.
+%%
+%%			* Options for PDF/A compliance. [pdf-a] will produce PDF/A-3u compliance with sRGB OutputIntent.
+%%			*	 [pdfapart= 1 or 2 or 3] and [pdfaconformance= b or u] can enable levels 1b, 2b, 2u, and 3b.
+%%			*    The most recent versions of LaTeX (2021 and later) are moving toward integrated support for pdf-a, 
+%%			*    through \DeclareDocumentMetadata{..}. The asmeconf class supports these new features, which can 
+%%			*	 replace the aforementioned class options. (An up-to-date LaTeX installation is required to use this.)
+%%
+%%          * Many options for calligraphic, script, and fraktur fonts from the mathalfa package; the
+%%          *    example shown here is: [mathalfa=cal=boondoxo] to use a Boondox font for \mathcal.
+%%          *    Some other options for cal are: dutchcal, zapfc, cm (default), euler,...
+%%          *    frak (fraktur), bb (blackboard bold), scr (script) may also be chosen this way.
+%%			*	 For details, refer to mathalfa documentation (at CTAN: http://ctan.org).
+%%
+%%          * Option to use superiors font from newtxtext for footnotes [nodefaultsups] and
+%%          *    for slightly larger small capitals, [largesc], also from newtxtext.
+%%
+%%          * An option to allow hyphenation of the typewriter font [hyphenate], from inconsolata package.
+%%          *    Hyphenation is normally suppressed for typewriter mode because it is often used for code.
+%%			*	 To replace the default variable word spacing by monospacing, use the option [mono].
+%%			*	 To get a zero without a slash, use [var0]
+%%
+%%          * Options (used by the babel package) to include passages in languages other than English (e.g., a translation 
+%%			*    of the abstract). Languages are called as options, e.g. [french], [spanish], [greek], [russian], etc. 
+%%			*    Language support is greatest when running LuaLaTeX with the [fontspec] option.
+%%			*    See Appendix B for details.
+%%
+%%  The use of commands defined or modified by the asmeconf class is illustrated throughout this file. In particular, 
+%%  ASME requires capitalized, sans-serif section headings, and as a result some care is needed when using macros 
+%%  in section headings, as also illustrated below.
+%%
+%%  Use an up-to-date and complete installation of LaTeX, such as TeX Live 2020 or later. Errors may occur with old set-ups.
+%%
+ %=========================================================
+%% 
+%% LICENSE: 
+%%
+%% Copyright (c) 2022 John H. Lienhard
+%%
+%% Offered under the MIT license: https://ctan.org/license/mit 
+%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%% Class options are described above. Change these options as desired. 
+%%		If you are not using the language options, remove them (together with Appendices B and C)
+%%	 	Remove the [colorlinks] option before *final* submission to ASME, to get black text for printing,
+%%		but keep that option for other uses.
+
+\documentclass[balance,upint,subscriptcorrection,varvw,mathalfa=cal=boondoxo,pdf-a,colorlinks,nofoot]{asmeconf}
 \usepackage{tikz}
 \usetikzlibrary{shapes.geometric, arrows.meta}
-\usepackage{hyperref}
-\geometry{margin=0.8in}
+\tikzstyle{process} = [rectangle, minimum width=2cm, minimum height=1.3cm, text centered, draw=black]
+\tikzstyle{arrow} = [thick,->,>={Stealth[scale=1.1]}]
+\usepackage{algorithm, algpseudocode}
+\usepackage{siunitx}
 \graphicspath{ {../data/} }
+%%%%%  pdf metadata  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-%\renewcommand{\familydefault}{\sfdefault}
-%\sisetup{output-exponent-marker=\ensuremath{\mathrm{e}}}
-\tikzstyle{process} = [rectangle, minimum width=2cm, minimum height=1.3cm, 
-text centered, draw=black]
-\tikzstyle{arrow} = [thick,->,>={Stealth[scale=1.1]}]
-
-\title{Reinforcement Learning Report}
-\author{Yuanhao JIANG}
-\date{}
+\hypersetup{%
+	pdfauthor={Yuanhao JIANG},
+	pdftitle={Mathematics of Reinforcement Learning with Applications to Quantitative Finance},
+	pdfkeywords={Reinforcement Learning,  Artificial Neural Networks},
+	pdfsubject={Describe Mathematics of Reinforcement Learning with Applications to Quantitative Finance},
+    pdfurl={https://github.com/Yuanhao-JIANG/RL-in-QF},
+%	pdflicenseurl={https://ctan.org/pkg/asmeconf},
+}
 
 \begin{document}
+
+% Change these fields to the right content for your conference.
+% You can comment these out if for some reason you don't want a header.
+% Use title case (first letters capitalized), not all capitals
+
+\ConfName{Proceedings of the ASME 2022\linebreak International Mechanical Engineering Congress and Exposition}
+\ConfAcronym{IMECE2022}
+\ConfDate{October 30--November 3, 2022} % update 
+\ConfCity{Columbus, OH} % update 
+\PaperNo{IMECE2022-XXXX}
+
+% Units of measure (e.g., cm) and other specialty lowercase terms in the title should be 
+%   enclosed in \NoCaseChange{...} to maintain lower case type
+%   LaTeX will automatically set the rest of the title in all capital letters.
+
+\title{Mathematics of Reinforcement Learning with Applications to Quantitative Finance}
+%\title{Place Title Here: Place Subtitle After Colon}
+
+%   Put author names into the order you want. Use the same order for affiliations.
+%   \affil{#} tags the author's affiliation to the address in \SetAffiliation{#}.
+%   No space between last name and \affil{#}, separate names with commas.
+%
+%	For a sole author or a single affiliation for all authors, {#} may be left empty, as \affil{} and \SetAffiliation{} (but not with [grid] option!)
+%
+%   \CorrespondingAuthor{email} follows that author's affiliation, no spaces.  
+%   If multiple corresponding authors, put both email addresses in the same command and place after both authors.
+%
+%   \JointFirstAuthor, if applicable, follows the affiliation of the relevant authors, no spaces.
+
+\SetAuthors{%
+	Yuanhao JIANG\affil{1}\JointFirstAuthor\CorrespondingAuthor{}, 
+	Luis Hern\'andez\affil{2}\JointFirstAuthor, 
+	Catherine~Parr\affil{3}\CorrespondingAuthor{s2132254@ed.ac.uk, kate@thepalace.gov}
+	}
+
+\SetAffiliation{1}{The University of Edinburgh, Edinburgh, UK}
+\SetAffiliation{2}{Institution or Company Name, City, State}
+\SetAffiliation{3}{Hampton Court Palace, Richmond, England}
+%	Note: Luis and Maria are not real people.  Henry and Catherine have been dead for >450 years.
+
+%	To switch from inline author names to gridded names, use the [grid] option.
+
 \maketitle
-\tableofcontents
+
+%%% Use this footnote for tracking various versions of your draft. Change text to suit your own needs. 
+%%% \date{..} calls the same command. 
+\versionfootnote{Documentation for \texttt{asmeconf.cls}: Version~\versionno, \today.}% <=== Delete before final submission.
+
+%%% Change these to your keywords.  Keywords are automatically printed at the end of the abstract.
+%%% This command MUST COME BEFORE the end of the abstract.
+%%% If you don't want keywords, leave the argument of \keywords{} empty (or use the abstract* environment)
+
+\keywords{Reinforcement Learning, Artificial Neural Networks}
+
+%%%%%  End of fields to be completed. Now write your paper. %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%  ABSTRACT  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%
+%% Abstract should be 200 words or less
+\begin{abstract}
+
+This paper is an example of and a  {\upshape\LaTeX} template for typesetting ASME conference papers using the {\upshape\texttt{asmeconf}} class.
+This  {\upshape\LaTeX} template follows ASME guidelines for margins, fonts, headings, captions, and reference formats as of 2022.
+The class is intended to be used with the {\upshape\texttt{asmeconf.bst} \hologo{BibTeX}} style for reference formatting, which is part of this distribution.
+The template produces pdfs that contain hyperlinks, bookmarks, and metadata; and references can include the DOI and URL fields.
+Links may be colored, for online use, or black, for publication.
+The class enables inline author names, following ASME's current style, but can also produce the traditional grid style.
+Options include line numbering, final column balancing, various math options, government copyright, and archivability (PDF/A).
+In addition, section headers may contain mathematics, references, citations, and footnotes.
+The class is compatible with {\upshape\hologo{pdfLaTeX}} or {\upshape\hologo{LuaLaTeX}}.
+\end{abstract}
+
+%%%%%%%%%  BODY OF PAPER %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 policy's parameter vector and value function's weight vector, respectively.
-Then we have our policy \(\pi\left(a\;\middle|\;s, \bm{\theta}\right)=
-\text{Pr}\left\{A_t=a\;\middle|\;S_t=s, \bm{\theta_t}=\bm{\theta}\right\}\) and
+Then we have our policy \(\pi\left(a\;\middle|\;s, \bm{\theta}\right)
+=\text{Pr}\left\{A_t=a\;\middle|\;S_t=s, \bm{\theta}_t=\bm{\theta}\right\}\) and
 value function \(v_\pi(s, \bm{w})\). We also define the scalar performance
@@
 including normal distribution, binomial distribution, and so on. For example, 
-a feature vector \(x\) is described as below:
-\begin{table}[htpb]
+a feature vector \(x\) is described as Table \ref{tab:1}
+\begin{table*}
+    \caption[Table]{Customer Feature Vector Description\label{tab:1}}
     \centering
@@
     \end{tabular}
-\end{table}
+\end{table*}
 
@@
 vector of a customer features vector \(x\) appended with a price \(c\), i.e.
-\(r=glm(x[0], \dots, x[14], c)\).
+\(r=glm(x[0], \dots, x[15], c)\).
 \vspace{3mm}\newline The GLM used in the project is fitted using a randomly
 generated data set with each observation is a customer's features followed by 
-a price, then followed by a resopnse e.g.
-\begin{table}[htpb]
+a price, then followed by a resopnse, as illustrated by Table \ref{tab:2}.
+\begin{table*}
+    \caption[Table]{Customer Feature Vector Description\label{tab:2}}
     \centering
@@
     \end{tabular}
-\end{table}
+\end{table*}
 
-\noindent And its link function is chose to be the logistic function.
+\vspace{3mm}\noindent And the link function for the GLM is chosen to be the logistic function.
 
@@
 In the end, the state \(s\), or \(s_t\) is of the form 
-\(s_t=(x_t[0],\:\dots,\:x_t[14],\:\text{avg\_pf}_t,\:\text{p}_t,
-\:\text{var}_t)\)
+\(s_t=(x'_t[0],\:\dots,\:x'_t[-1],\:\text{avg\_pf}_t,\:\text{p}_t,
+\:\text{var}_t)\), where \(x'_t\) is the modified \(x_t\), including preprocess
+of converting some categorical data to meaningful data to the model.
 
@@
 \subsection{Training Result}
-The following graph shows the training result of the above algorithm (300
+Figure \ref{fig:1} shows the training result of the above algorithm (300
 moving average reward vs iteration), with 600 iterations (5 episodes per
@@
 \(\alpha_\theta=\alpha_{\bm{w}}=\num{3e-4}\).
-\begin{center}
-    \includegraphics[scale=0.67]{a2c_out}
-\end{center}
+\begin{figure*}
+    \centering\includegraphics[scale=0.67]{a2c_out}
+    \caption{Training Result for Algorithm a2c\label{fig:1}}
+\end{figure*}
 The graph shows that the moving average reward converges within only 50
@@
 is true for the value function used in PPO method.
-\vspace{3mm}\newline The following graph shows the training result of these 
+\vspace{3mm}\newline Figure \ref{fig:2} shows the training result of these
 three algorithms (300 moving average reward vs iteration), with 600 iterations
@@
 \(\epsilon=0.5\) (if applicable).
-\begin{center}
-    \includegraphics[scale=0.67]{out}
-\end{center}
-As is shown in the graph, the Actor-Critic algorithm converges the fastest,
+\begin{figure*}
+    \centering\includegraphics[scale=0.67]{out}
+    \caption{Training Result Comparison for Three Algorithm\label{fig:2}}
+\end{figure*}
+As is shown in Figure \ref{fig:2}, the Actor-Critic algorithm converges the fastest,
 within 50 iterations, followed by Reinforce algorithm, which converges within
@@
 
+\section{Conclusion}
+Provide a brief conclusion (3-4 lines).
+
+\section*{Acknowledgments}
+Place any acknowledgments here.
+
+%%%  REFERENCES  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%
+%% Put your references into your .bib file in the usual way. Run latex once, bibtex once, then latex twice.
+%% The asmeconf.bst style allows @inproceedings and @proceedings to include: 
+%%		venue = {Location of Conference}, 
+%%		eventdate = {Month, days},
+
+\nocite{*}%% <=== Delete this line unless you want to typeset the entire contents of your .bib file!
+
+\bibliographystyle{asmeconf}  %% .bst file following ASME conference format. Do not change.
+\bibliography{paper_2-col}
+
+%%%  APPENDICES  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\appendix
+
+%% Note that appendices will be "numbered" A, B, C, ... etc. Use \section, not \section*
+%% Equations will be numbered sequentially following those in the paper. Do not reset the equation counter.
+
+%% Here we use the optional argument to control the pdf bookmark and prevent errors.
+\section[The Vector Product A\times B]{The vector product $\vec{A}\times\vec{B}$}\label{appendix:a}
+
+This brief illustration of an appendix shows the numbering of the appendix and equations. Equations are numbered
+consecutively, following those in the paper. Consider $\rho \neq \textrm{fn}(p)$:
+\begin{align}
+\frac{d\Gamma}{dt} &{}= \frac{d}{dt} \int_{\mathcal{C}} \mathbf{u} \cdot d\mathbf{r}\\
+				   &{}= \int_{\mathcal{C}} \frac{D\mathbf{u}}{Dt} \cdot d\mathbf{r} + \underbrace{\int_{\mathcal{C}} \mathbf{u}\cdot d\biggl( \frac{d\mathbf{r}}{dt}\Biggr)}_{=\, 0} \\[-2pt]
+                   &{}= \iint_{\mathcal{S}} \nabla \times \frac{D\mathbf{u}}{Dt}  \cdot d\mathbf{A}\\
+                   &{}= \iint_{\mathcal{S}}  \nabla p \times \nabla \left( \frac{1}{\rho}\right) \cdot d\mathbf{A}
+\end{align}
+
 \end{document}

### 2022-08-18 papers/paper_2-col.tex
update format and fix bugs

@@
 \begin{abstract}
-
-This paper is an example of and a  {\upshape\LaTeX} template for typesetting ASME conference papers using the {\upshape\texttt{asmeconf}} class.
+\noindent This paper is an example of and a  {\upshape\LaTeX} template for typesetting ASME conference papers using the {\upshape\texttt{asmeconf}} class.
 This  {\upshape\LaTeX} template follows ASME guidelines for margins, fonts, headings, captions, and reference formats as of 2022.
@@
 
-%%%%%%%%%  BODY OF PAPER %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \section{Introduction}
-The object is to use reinforcement learning to solve the following scenario:
+\noindent The object is to use reinforcement learning to solve the following scenario:
 a customer arrives with a number of features, we want to promote the customer
@@
 \section{Reinforcement Learning}
-The reinforcement learning method we want to use is based on the Markov 
-decision process (MDP), as illustrated below:
-\begin{center}
+\noindent The reinforcement learning method we want to use is based on the Markov 
+decision process (MDP), as illustrated in Figure~\ref{fig:MDP-illustration}.
+\begin{figure}
+    \centering
     \begin{tikzpicture}
@@
             {\(R_{t+1}\)} coordinate(a2);
-        \draw [arrow] (a2) -- ++(-1.3,0) -- ++(0,3.2) 
-            -- node[anchor=south, xshift=0.5cm] {\(R_t\)} (agent.154);
+        \draw [arrow] (a2) -- ++(-1.3,0) -- ++(0,3) 
+            -- node[anchor=south, xshift=0.5cm] {\(R_t\)} (agent.159);
         \draw [arrow] (pi) -- ++(2.7,0) node[anchor=south, xshift=-0.8cm] 
@@
     \end{tikzpicture}
-
-\end{center}
+    \caption{MDP Illustration}
+    \label{fig:MDP-illustration}
+\end{figure}
 \noindent However, in RL, the agent is not told which actions to take, but 
@@
 \subsection{Policy Evaluation}
-We want to evaluate the value function under a given policy \(\pi\). According 
-to Bellman equation,
+\noindent We want to evaluate the value function under a given policy \(\pi\).
+According to Bellman equation,
 \[v_\pi(s)=\mathbb{E}_\pi\left[R_{t+1}+\gamma v_\pi(S_{t+1})\;\middle|\;
@@
 \subsection{Policy Improvement}
-Now we have the evaluated value function for the policy, we want to improve it
-accordingly. To do this, we introduce the q-function under policy \(\pi\)
+\noindent Now we have the evaluated value function for the policy, we want to 
+improve it accordingly. To do this, we introduce the q-function under 
+policy \(\pi\)
 \[q_\pi(s, a) = \mathbb{E}\left[R_{t+1} + \gamma v_\pi(S_{t+1})\;\middle|\;
@@
 \subsection{Policy Iteration}
-By iteratively applying policy evaluation and policy improvement, we can obtain
-a sequence of monotonically improving policies and value functions:
+\noindent By iteratively applying policy evaluation and policy improvement, we
+can obtain a sequence of monotonically improving policies and value functions:
 \[\pi_0 \overset{E}{\longrightarrow} v_{\pi_0} \overset{I}{\longrightarrow}
@@
 \subsection{Value Iteration}
-One drawback to policy iteration is that each of its iterations involves policy
-evaluation, which itself is a protracted iterative computation requiring
-multiple sweeps through the state set.
+\noindent One drawback to policy iteration is that each of its iterations 
+involves policy evaluation, which itself is a protracted iterative computation
+requiring multiple sweeps through the state set.
 \vspace{3mm}\newline We now truncate the policy evaluation such that it is
@@
 \subsection{Generalized Policy Iteration}
-As long as both processes, policy evaluation and policy improvement, continue
-to update all states, the ultimate result is typically the same --- converge to
-the optimal value function and an optimal policy.
+\noindent As long as both processes, policy evaluation and policy improvement,
+continue to update all states, the ultimate result is typically the 
+same --- converge to the optimal value function and an optimal policy.
 \vspace{3mm}\newline Generalized policy iteration (GPI) is used to refer to the
@@
 \subsection{Temporal-Difference Learning}
-When we don't have the complete model of the environment, we need to estimate 
-the value function from only experience. There are two methods to do so: 
-Monte Carlo Methods and Temporal-Difference. We will use Temporal-Difference
-method in this project.
+\noindent When we don't have the complete model of the environment, we need to 
+estimate the value function from only experience. There are two methods to do 
+so: Monte Carlo Methods and Temporal-Difference. We will use 
+Temporal-Difference method in this project.
 \vspace{3mm}\newline To estimate \(v_\pi(S_t)\) using only the experience, we 
@@
 \subsection{Policy Gradient Methods}
-When the state space is arbitrarily large, we cannot find an optimal policy or
-the optimal value function given the limited resources and time. Instead of
-keeping track of the value and the action(s) to select for each state (tabular
-methods), we can use parameterized functions, for example, artificial neural
-networks (ANNs), to approximate the value function and the policy function.
+\noindent When the state space is arbitrarily large, we cannot find an optimal 
+policy or the optimal value function given the limited resources and time. 
+Instead of keeping track of the value and the action(s) to select for each 
+state (tabular methods), we can use parameterized functions, for example, 
+artificial neural networks (ANNs), to approximate the value function and the 
+policy function.
 \vspace{3mm}\newline Previously methods learned the values of actions and then
@@
 \end{align*}
-The actor-critic method is based on the above updates formulas:
-\begin{algorithm}[H]
-\caption{Actor-Critic}
+The actor-critic method is based on the above updates formulas, details are
+shown in Algorithm \ref{algorithm:actor-critic}.
+\begin{algorithm}
+    \caption{Actor-Critic\label{algorithm:actor-critic}}
     \begin{algorithmic}[1]
@@
 \section{Build the Environment}
-The environment does the following things:
+\noindent The environment does the following things:
 \begin{enumerate}
@@
 \subsection{Customer Features}
-A customer' features is represented by an array (or vector), denoted by \(x\) 
-with 16 entries with each generated randomly from a distribution, 
+\noindent A customer's features is represented by an array (or vector), denoted 
+by \(x\) with 16 entries with each generated randomly from a distribution, 
 including normal distribution, binomial distribution, and so on. For example, 
@@
 \subsection{Resopnse}
-The resopnse is generated by a generalized linear model, whose input is a 
-vector of a customer features vector \(x\) appended with a price \(c\), i.e.
-\(r=glm(x[0], \dots, x[15], c)\).
+\noindent The resopnse is generated by a generalized linear model, whose input 
+is a vector of a customer features vector \(x\) appended with a price \(c\), 
+i.e. \(r=glm(x[0], \dots, x[15], c)\).
 \vspace{3mm}\newline The GLM used in the project is fitted using a randomly
@@
 \subsection{State}
-The state at start of each time step is the feature vector of the new customer 
-to promote (might be modified a bit), appended by the portfolio, which is also 
-a data vector consists of the following entries:
+\noindent The state at start of each time step is the feature vector of the 
+new customer to promote (might be modified a bit), appended by the portfolio, 
+which is also a data vector consists of the following entries:
 \begin{itemize}
@@
         make sure the agent will promote to all types of customers instead of 
-        only focusing on one type.
-        \vspace{2mm}\newline Note that \(\text{var}\leq1\).
+        only focusing on one type. Note that \(\text{var}\leq1\).
 \end{itemize}
-In the end, the state \(s\), or \(s_t\) is of the form 
+Thus, the state \(s\), or \(s_t\), end up with the form 
 \(s_t=(x'_t[0],\:\dots,\:x'_t[-1],\:\text{avg\_pf}_t,\:\text{p}_t,
@@
 \subsection{Reward}
-The reward at each time step \(t\), after the price \(c_t\) is promoted to the 
-customer \(x_t\), denoted by \(R_t\), is calculated by
+\noindent The reward at each time step \(t\), after the price \(c_t\) is 
+promoted to the customer \(x_t\), denoted by \(R_t\), is calculated by
 \[R_t = \text{pf}_t\left(1-h(\text{var}_t)\right)\]
@@
 \section{Build the model}
-With the environment well built, we now build the model for our policy and the
-value function. In this project we use artificial neuro networks (ANNs) as the 
-parameterized policy and value function, each with three linear layers, and 
-with the ReLU function as the activation function. And the input of both 
-function is the state, as illustrated below:
+\noindent With the environment well built, we now build the model for our 
+policy and the value function. In this project we use artificial neuro networks
+(ANNs) as the parameterized policy and value function, each with three linear 
+layers, and with the ReLU function as the activation function. And the input 
+of both function is the state, as illustrated in Figure~\ref{fig:ANN}.
+\begin{figure*}
+    \centering
     \[S_t\rightarrow\underset{\text{ANN for value function}}{
@@
     }\rightarrow \pi_t\rightarrow c_t\]
+    \caption{ANN model for policy and value function\label{fig:ANN}}
+\end{figure*}
 where \(n(S)\) denotes the vector length of the state and \(n(A)\) denotes 
@@
 \section{RL with Actor-Critic}
+\noindent In this project, we consider the episodic learning procedure, where 
+each episode has finite time steps, \(T\), to be specified as a constant, and 
+we will also reset the environment at the start of each episode.
+
 \subsection{The Algorithm}
-In this project, we consider the episodic learning procedure, where each
-episode has finite time steps, \(T\), to be specified as a constant, and we
-will also reset the environment at the start of each episode. The algorithm
-below is to use RL, with actor-critic method, and with the help of what we
-have built in previous sections, to solve the problem:
-\begin{algorithm}[H]
-\caption{Actor-Critic for our financial problem}
+\noindent Algorithm \ref{algorithm:actor-critic-fin} uses RL with actor-critic 
+method, and with the help of what we have built in previous sections, to solve 
+the problem.
+\begin{algorithm}
+    \caption{Actor-Critic for our financial problem
+        \label{algorithm:actor-critic-fin}
+    }
     \begin{algorithmic}[1]
@@
 \end{algorithm}
-\noindent The following graph illustrates the algorithm:
-\vspace{5mm}
-\begin{center}
+\noindent Figure~\ref{fig:a2c-illustration} illustrates the algorithm.
+\begin{figure}
+    \centering
     \begin{tikzpicture}[node distance=2cm]
@@
     \end{tikzpicture}
-\end{center}
+    \caption{Actor-Critic for Finance Algorithm Illustration}
+    \label{fig:a2c-illustration}
+\end{figure}
 
 \subsection{Training Result}
-Figure \ref{fig:1} shows the training result of the above algorithm (300
-moving average reward vs iteration), with 600 iterations (5 episodes per
-iteration), \(T=300\), \(\gamma=0.99\),
-\(\alpha_\theta=\alpha_{\bm{w}}=\num{3e-4}\).
+\noindent Figure~\ref{fig:a2c-out} shows the training result of 
+Algorithm~\ref{algorithm:actor-critic} (300 moving average reward vs 
+iteration), with 600 iterations (5 episodes per iteration), \(T=300\), 
+\(\gamma=0.99\), \(\alpha_\theta=\alpha_{\bm{w}}=\num{3e-4}\).
 \begin{figure*}
-    \centering\includegraphics[scale=0.67]{a2c_out}
-    \caption{Training Result for Algorithm a2c\label{fig:1}}
+    \centering\includegraphics[scale=0.75]{a2c_out}
+    \caption{Training Result for Algorithm a2c}
+    \label{fig:a2c-out}
 \end{figure*}
@@
 \subsection{Algorithms}
-To further show how Actor-Critic algorithm performs, we compare it to another
-two popular algorithms: Reinforce and PPO. Below are pseudocodes for the two
-algorithms:
-\begin{algorithm}[H]
-\caption{Reinforce for our financial problem}
+\noindent To further show how Actor-Critic algorithm performs, we compare it 
+to another two popular algorithms: Reinforce 
+(Algorithm~\ref{algorithm:reinforce}) and PPO (Algorithm~\ref{algorithm:ppo}).
+\begin{algorithm}
+    \caption{Reinforce for our financial problem}\label{algorithm:reinforce}
     \begin{algorithmic}[1]
@@
         \State Reset the environment
-    \State Generate an episode \(S_0, C_0, R_1, ..., S_{T-1}, C_{T-1}, R_T\),
+        \State Generate an episode 
+        \(S_0, C_0, R_1, ..., S_{T-1}, C_{T-1}, R_T\),
         following \(\pi\left(\cdot\middle|\cdot, \bm{\theta}\right)\)
@@
 
-\begin{algorithm}[H]
-\caption{PPO for our financial problem}
+\begin{algorithm*}
+    \caption{PPO for our financial problem}\label{algorithm:ppo}
     \begin{algorithmic}[1]
@@
         \(\tau = S_0, C_0, R_1, ..., S_{T-1}, C_{T-1}, R_T\)
-    \For{\(t=0, 1, ..., T\) in each trajectory \(\tau\) in \(\mathcal{D}_k\)}
+        \For{\(t=0, 1, ..., T\) in each trajectory \(\tau\) in 
+        \(\mathcal{D}_k\)}
         \State \(G_t \gets \sum_{k=t+1}^{T} \gamma^{k-t-1}R_k\)
@@
         \State \(\bm{\theta} \gets \underset{\bm{\theta}}{\text{arg\:max}}
-    \frac{1}{|\mathcal{D}_k|T}\sum_{\tau\in\mathcal{D}_k}^{} \sum_{t=0}^{T}
+        \frac{1}{|\mathcal{D}_k|T}
+        \sum_{\tau\in\mathcal{D}_k}^{} \sum_{t=0}^{T}
         \min{\left(
@@
     \end{algorithmic}
-\end{algorithm}
+\end{algorithm*}
 
 \subsection{Training result}
-To make better comparison, the policy function of the two algorithms
+\noindent To make better comparison, the policy function of the two algorithms
 is implemented the same way as we did in Actor-Critic algorithm, and the same
 is true for the value function used in PPO method.
-\vspace{3mm}\newline Figure \ref{fig:2} shows the training result of these
-three algorithms (300 moving average reward vs iteration), with 600 iterations
-(5 episodes per iteration), \(T=300\), \(\gamma=0.99\),
+\vspace{3mm}\newline Figure~\ref{fig:3-algorithms-out} shows the training 
+result of these three algorithms (300 moving average reward vs iteration), 
+with 600 iterations (5 episodes per iteration), \(T=300\), \(\gamma=0.99\),
 \(\alpha_\theta=\num{3e-4}\), \(\alpha_{\bm{w}}=\num{3e-10}\) (if applicable),
@@
 \begin{figure*}
-    \centering\includegraphics[scale=0.67]{out}
-    \caption{Training Result Comparison for Three Algorithm\label{fig:2}}
+    \centering\includegraphics[scale=0.75]{out}
+    \caption{Training Result Comparison for Three Algorithm}
+    \label{fig:3-algorithms-out}
 \end{figure*}
-As is shown in Figure \ref{fig:2}, the Actor-Critic algorithm converges the fastest,
-within 50 iterations, followed by Reinforce algorithm, which converges within
-about 250 iterations, despite a small drop of moving average around iteration
-300, which is quickly corrected by the algorithm within 50 iterations. PPO
-algorithm converges the slowest, with about 300 iterations. Despite of the
-speed of convergence, the moving average rewards of convergence for these
-three algorithms are nearly the same (around 400), this is as expected.
+As is shown in Figure~\ref{fig:3-algorithms-out}, the Actor-Critic algorithm 
+converges the fastest, within 50 iterations, followed by Reinforce algorithm, 
+which converges within about 250 iterations, despite a small drop of moving 
+average around iteration 300, which is quickly corrected by the algorithm 
+within 50 iterations. PPO algorithm converges the slowest, with about 300 
+iterations. Despite of the speed of convergence, the moving average rewards 
+of convergence for these three algorithms are nearly the same (around 400), 
+this is as expected.
 
 \section{Conclusion}
-Provide a brief conclusion (3-4 lines).
+\noindent Provide a brief conclusion (3-4 lines).
 
 \section*{Acknowledgments}
-Place any acknowledgments here.
+\noindent Place any acknowledgments here.
 

### 2022-08-19 papers/paper_2-col.tex
update author and bibliography

@@
 \SetAuthors{%
-	Yuanhao JIANG\affil{1}\JointFirstAuthor\CorrespondingAuthor{}, 
-	Luis Hern\'andez\affil{2}\JointFirstAuthor, 
-	Catherine~Parr\affil{3}\CorrespondingAuthor{s2132254@ed.ac.uk, kate@thepalace.gov}
+	Yuanhao JIANG\affil{1}\CorrespondingAuthor{s2132254@ed.ac.uk}
 	}
@@
 \SetAffiliation{1}{The University of Edinburgh, Edinburgh, UK}
-\SetAffiliation{2}{Institution or Company Name, City, State}
-\SetAffiliation{3}{Hampton Court Palace, Richmond, England}
 %	Note: Luis and Maria are not real people.  Henry and Catherine have been dead for >450 years.
@@
 \maketitle
-
-%%% Use this footnote for tracking various versions of your draft. Change text to suit your own needs. 
-%%% \date{..} calls the same command. 
-\versionfootnote{Documentation for \texttt{asmeconf.cls}: Version~\versionno, \today.}% <=== Delete before final submission.
 
@@
 \begin{abstract}
-\noindent This paper is an example of and a  {\upshape\LaTeX} template for typesetting ASME conference papers using the {\upshape\texttt{asmeconf}} class.
-This  {\upshape\LaTeX} template follows ASME guidelines for margins, fonts, headings, captions, and reference formats as of 2022.
-The class is intended to be used with the {\upshape\texttt{asmeconf.bst} \hologo{BibTeX}} style for reference formatting, which is part of this distribution.
-The template produces pdfs that contain hyperlinks, bookmarks, and metadata; and references can include the DOI and URL fields.
-Links may be colored, for online use, or black, for publication.
-The class enables inline author names, following ASME's current style, but can also produce the traditional grid style.
-Options include line numbering, final column balancing, various math options, government copyright, and archivability (PDF/A).
-In addition, section headers may contain mathematics, references, citations, and footnotes.
-The class is compatible with {\upshape\hologo{pdfLaTeX}} or {\upshape\hologo{LuaLaTeX}}.
+\noindent Abstract goes here.
 \end{abstract}
@@
 
-%%%  APPENDICES  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\appendix
-
-%% Note that appendices will be "numbered" A, B, C, ... etc. Use \section, not \section*
-%% Equations will be numbered sequentially following those in the paper. Do not reset the equation counter.
-
-%% Here we use the optional argument to control the pdf bookmark and prevent errors.
-\section[The Vector Product A\times B]{The vector product $\vec{A}\times\vec{B}$}\label{appendix:a}
-
-This brief illustration of an appendix shows the numbering of the appendix and equations. Equations are numbered
-consecutively, following those in the paper. Consider $\rho \neq \textrm{fn}(p)$:
-\begin{align}
-\frac{d\Gamma}{dt} &{}= \frac{d}{dt} \int_{\mathcal{C}} \mathbf{u} \cdot d\mathbf{r}\\
-				   &{}= \int_{\mathcal{C}} \frac{D\mathbf{u}}{Dt} \cdot d\mathbf{r} + \underbrace{\int_{\mathcal{C}} \mathbf{u}\cdot d\biggl( \frac{d\mathbf{r}}{dt}\Biggr)}_{=\, 0} \\[-2pt]
-                   &{}= \iint_{\mathcal{S}} \nabla \times \frac{D\mathbf{u}}{Dt}  \cdot d\mathbf{A}\\
-                   &{}= \iint_{\mathcal{S}}  \nabla p \times \nabla \left( \frac{1}{\rho}\right) \cdot d\mathbf{A}
-\end{align}
-
 \end{document}

### 2022-08-20 papers/paper_2-col.tex
update formatting and fix latex warnings

@@
 \begin{document}
-
 % Change these fields to the right content for your conference.
@@
 % Use title case (first letters capitalized), not all capitals
-
 \ConfName{Proceedings of the ASME 2022\linebreak International Mechanical Engineering Congress and Exposition}
@@
 %   \JointFirstAuthor, if applicable, follows the affiliation of the relevant authors, no spaces.
-
-\SetAuthors{%
+\SetAuthors{
 	Yuanhao JIANG\affil{1}\CorrespondingAuthor{s2132254@ed.ac.uk}
@@
 \SetAffiliation{1}{The University of Edinburgh, Edinburgh, UK}
-%	Note: Luis and Maria are not real people.  Henry and Catherine have been dead for >450 years.
-
 %	To switch from inline author names to gridded names, use the [grid] option.
@@
 %%% If you don't want keywords, leave the argument of \keywords{} empty (or use the abstract* environment)
-
 \keywords{Reinforcement Learning, Artificial Neural Networks}
 
-%%%%%  End of fields to be completed. Now write your paper. %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%  ABSTRACT  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%
 %% Abstract should be 200 words or less
@@
 \begin{align*}
-    [v_\pi(S_t)]_{k+1} &= \frac{1}{k}\sum_{i=1}^{k} G_i\\
-               &= \frac{1}{k}\left(G_k + \sum_{i=1}^{k-1} G_i\right)\\
-               &= \frac{1}{k}\left(G_k + (k-1)[v_\pi(S_t)]_{k}\right)\\
-               &= [v_\pi(S_t)]_k + \frac{1}{k}(G_k-[v_\pi(S_t)]_k)\\
-               &= [v_\pi(S_t)]_k + \frac{1}{k}
+    &[v_\pi(S_t)]_{k+1} \\
+    =\:& \frac{1}{k}\sum_{i=1}^{k} G_i\\
+    =\:& \frac{1}{k}\left(G_k + \sum_{i=1}^{k-1} G_i\right)\\
+    =\:& \frac{1}{k}\left(G_k + (k-1)[v_\pi(S_t)]_{k}\right)\\
+    =\:& [v_\pi(S_t)]_k + \frac{1}{k}(G_k-[v_\pi(S_t)]_k)\\
+    =\:& [v_\pi(S_t)]_k + \frac{1}{k}
     ([R_{t+1}]_k+\gamma [v_\pi(S_{t+1})]_k-[v_\pi(S_t)]_k)
@@
 with \(\alpha\) being the stepsize. And this also applies to the q function:
-\[q_\pi(S_t, A_t)\longleftarrow q_\pi(S_t, A_t)+\alpha
-[R_{t+1}+\gamma q_\pi(S_{t+1}, A_{t+1})-q_\pi(S_t, A_t)]\]
+\begin{multline*}
+    q_\pi(S_t, A_t)\longleftarrow q_\pi(S_t, A_t)\\
+    +\alpha[R_{t+1}+\gamma q_\pi(S_{t+1}, A_{t+1})-q_\pi(S_t, A_t)]
+\end{multline*}
 
@@
 Thus, the state \(s\), or \(s_t\), end up with the form
-\(s_t=(x'_t[0],\:\dots,\:x'_t[-1],\:\text{avg\_pf}_t,\:\text{p}_t,
-\:\text{var}_t)\), where \(x'_t\) is the modified \(x_t\), including preprocess
+\[s_t=
+(x'_t[0],\:\dots,\:x'_t[-1],\:\text{avg\_pf}_t,\:\text{p}_t, \:\text{var}_t)\]
+where \(x'_t\) is the modified \(x_t\), including preprocess
 of converting some categorical data to meaningful data to the model.
@@
 \begin{algorithm}
-    \caption{Actor-Critic for our financial problem
+    \caption{Actor-Critic for financial problem
         \label{algorithm:actor-critic-fin}
@@
 \end{algorithm}
-\noindent Figure~\ref{fig:a2c-illustration} illustrates the algorithm.
+\noindent And Figure~\ref{fig:a2c-illustration} illustrates the algorithm.
 \begin{figure}
@@
             {\(\hat{v}\left(s,\bm{w}\right)\)};
-        \node (env) [process, below of=pi, yshift=-2.5cm] {Environment};
+        \node (env) [process, below of=pi, yshift=-2cm] {Environment};
 
@@
         \draw [arrow] (env)
-            -- ++(0,-2.3) node[anchor=east, yshift=0.8cm] {\(S_{t+1}\)}
+            -- ++(0,-1.7) node[anchor=east, yshift=0.5cm] {\(S_{t+1}\)}
             -- ++(-1.5,0) coordinate(next_s);
-        \draw [arrow] (next_s) -- ++(-1,0) -- ++ (0,10) -- ++(4,0)
+        \draw [arrow] (next_s) -- ++(-1,0) -- ++ (0,8.7) -- ++(4,0)
             -- ++(0,-1.7)
-            node[anchor=east, yshift=0.9cm] {\(S_t\)} coordinate(m1)
+            node[anchor=east, yshift=1cm] {\(S_t\)} coordinate(m1)
             -- (pi.93);
@@
         \draw [dashed,arrow] (m4) -- (v);
-        \draw [dashed, thick] (-3,-6.5) -- (-3,-7.8);
+        \draw [dashed, thick] (-3,-5.4) -- (-3,-6.7);
     \end{tikzpicture}
@@
 \begin{algorithm}
-    \caption{Reinforce for our financial problem}\label{algorithm:reinforce}
+    \caption{Reinforce for financial problem}\label{algorithm:reinforce}
     \begin{algorithmic}[1]
@@
 \begin{algorithm*}
-    \caption{PPO for our financial problem}\label{algorithm:ppo}
+    \caption{PPO for financial problem}\label{algorithm:ppo}
     \begin{algorithmic}[1]

### 2022-08-22 papers/paper_2-col.tex
update abstract and introduction

@@
 %%% If you don't want keywords, leave the argument of \keywords{} empty (or use the abstract* environment)
-\keywords{Reinforcement Learning, Artificial Neural Networks}
+\keywords{
+    Reinforcement Learning, Artificial Neural Networks, Quantitative Finance
+}
 
@@
 \begin{abstract}
-\noindent Abstract goes here.
+\noindent This paper provides a new way of pricing in the car insurance
+industry, which is, using reinforcement learning algorithms to train pricing 
+agents to promote proper price, such that our customer is most likely to 
+purchase our product, and we also get the highest profit and a better 
+portfolio. 
+We first introduce general reinforcement learning knowledge, including how 
+we model the interaction between agent and environment using MDP, and the 
+mathematics behind those methods to solve the reinforcement learning problem, 
+especially the Actor-Critic algorithm.
+Then we start building the environment, and use ANNs as our pricing models, 
+and writing algorithms that are specific to our financial problem. 
+In the end, we will compare and discuss different algorithms in terms of their
+rate of convergence to a stable reward.
 \end{abstract}
@@
 \section{Introduction}
-\noindent The object is to use reinforcement learning to solve the following scenario:
-a customer arrives with a number of features, we want to promote the customer
-with a proper price, such that he is most likely to purchase our product, and 
-we also have the highest profit and a better portfolio. 
-\vspace{3mm}\newline We can consider this scenario as markov decision process,
-with the current state being the current customer features and current 
-portfolio. At each time step, the agent promote a price according to the 
-current customer features and the current portfolio, after that the customer 
-resopnse to the action. The reward is then given besed on the customer 
-response and the portfolio. Then the portfolio updates and a new customer 
-arrives.
+\noindent Modern way of calculating car insurance premium is by estimating
+how much risk the customer poses to the insurance provider, and more risk 
+results in higher premium. 
+The estimation of the risk for a customer is usually done by comparing various
+risk factors with the statistics of the database collected so far. Those 
+factors might include customer's age, address, occupation, car's mileage, 
+brand and model, and so on. For example, younger drivers pose higher risks 
+since they are more likely to have an accident due to the lack of driving 
+experience compare to elder drivers.
+\vspace{2mm}\newline In this paper, instead of using the above method to 
+promote car insurance, we use RL methods to train agents that will interact 
+with the market and response with price. More specifically, we consider the 
+insurance promoting scenario as markov decision process, with the current 
+state being the current customer features and current portfolio. At each time
+step, the agent promote a price according to the current customer features and
+the current portfolio, after that the customer resopnse to the promotion. The 
+reward is then given besed on the customer response and the portfolio. Then 
+the portfolio updates and a new customer arrives. This set up will help us to
+solve the poblem in the context of reinforcement learning, further details are
+discussed in the remaining sections.
 

### 2022-08-22 papers/paper_2-col.tex
write up conclusion

@@
 We first introduce general reinforcement learning knowledge, including how 
-we model the interaction between agent and environment using MDP, and the 
-mathematics behind those methods to solve the reinforcement learning problem, 
-especially the Actor-Critic algorithm.
-Then we start building the environment, and use ANNs as our pricing models, 
-and writing algorithms that are specific to our financial problem. 
-In the end, we will compare and discuss different algorithms in terms of their
-rate of convergence to a stable reward.
+we model the interaction between agent and environment using Markov decision
+process, and the mathematics behind those methods to solve the reinforcement 
+learning problem, especially the Actor-Critic algorithm.
+Then we start building the environment, and use artificial neural networks as 
+our pricing models, and writing algorithms that are specific to our financial 
+problem. 
+In the end, we will compare the Actor-Critic algorithms with other popular 
+algorithms including REINFORCE and PPO in terms of their rate of convergence 
+to a stable reward.
 \end{abstract}
@@
 (Algorithm~\ref{algorithm:reinforce}) and PPO (Algorithm~\ref{algorithm:ppo}).
+The policy function of the two algorithms is implemented the same way as we 
+did in Actor-Critic algorithm, and the same is true for the value function 
+used in PPO method.
 \begin{algorithm}
@@
 \subsection{Training result}
-\noindent To make better comparison, the policy function of the two algorithms
-is implemented the same way as we did in Actor-Critic algorithm, and the same
-is true for the value function used in PPO method.
-\vspace{3mm}\newline Figure~\ref{fig:3-algorithms-out} shows the training 
+\noindent Figure~\ref{fig:3-algorithms-out} shows the training 
 result of these three algorithms (300 moving average reward vs iteration), 
@@
 \end{figure*}
-As is shown in Figure~\ref{fig:3-algorithms-out}, the Actor-Critic algorithm 
-converges the fastest, within 50 iterations, followed by Reinforce algorithm, 
-which converges within about 250 iterations, despite a small drop of moving 
-average around iteration 300, which is quickly corrected by the algorithm 
-within 50 iterations. PPO algorithm converges the slowest, with about 300 
-iterations. Despite of the speed of convergence, the moving average rewards 
-of convergence for these three algorithms are nearly the same (around 400), 
-this is as expected.
+As we can see, the Actor-Critic algorithm converges the fastest, within 50 
+iterations, followed by REINFORCE algorithm, which converges within 250 
+iterations, despite a small drop of moving average around iteration 300, 
+which is quickly corrected by the algorithm within 50 iterations. PPO 
+algorithm converges the slowest, with about 300 iterations.
 
 \section{Conclusion}
-\noindent Provide a brief conclusion (3-4 lines).
+\noindent To summarize, the moving average rewards after convergence of these 
+three algorithms are nearly the same (around 400), which is as expected. 
+The Actor-Critic algorithm performs really well compared to anther two 
+algorithms, it has highest converge rate, the reward is also very stable after 
+convergence. 
+In the mean time, the slow convergence for PPO algorithm is expected since it 
+uses a clamp function to prevent model from changing too fast in a single 
+update, although at current stage it seems to be unnecessary for our specific 
+problem setup. 
+Further investigation needs to be done for the unexpected small drop of the 
+reward for the REINFORCE algorithm.
 

### 2022-08-23 papers/paper_2-col.tex
add reference and re-format paper

@@
-% !TEX encoding = UTF-8 Unicode
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-%%
-%%  This file is asmeconf-template.tex, a LaTeX template to format ASME Conference papers according to
-%%  the requirements on ASME's conference web pages, and including hypertext support for the pdf.
-%%
-%%  This file is version 1.31 dated 2022/07/04
-%%  
-%%  As of version 1.11, this template defaults to ASME's newer conference guidelines first posted July 2019.
-%% 			Those guidelines changed the requested author block formatting to be inline. 
-%%			This LaTeX template continues to support the traditional grid format as a package option, [grid].
-%%			Nomenclature now follows the abstract. Abstract text is set in italics.
-%%
-%%  Author: John H. Lienhard V
-%%          Department of Mechanical Engineering
-%%          Massachusetts Institute of Technology
-%%          Cambridge, MA 02139-4307 USA
-%%
-%%  Class options include:
-%%
-%%          * Math options from M. Sharpe's newtxmath package: upright integrals [upint]; 
-%%          *    [varvw] for a v and w that are better distinguished from Greek nu; and also 
-%%          *    [subscriptcorrection, smallerops, varg, frenchmath, varbb, cmbraces, slantedGreek,...] 
-%%			* 	 See newtx documentation for descriptions (at CTAN: http://ctan.org, v1.6 or higher is best).
-%%
-%%          * Options to: 	omit the ASME copyright footer [nofoot]; 
-%%			*				use government employee copyright notice [govt];
-%%			*				use government contractor copyright notice [contractor]
-%%
-%%          * An option to use the traditional grid arrangement of author names [grid].  
-%%			*	 With this option, line breaks (\\) may be inserted into the address as needed. 
-%%			*	 Author names that include commas should be enclosed in braces, e.g., {Joseph L. Smith, Jr.}.  
-%%			*	 Authors may be grouped above a single affiliation using braces, e.g., {Henry Tudor, Catherine Parr}.
-%%
-%%          * An option to balance the heights of columns on the last page [balance]. 
-%%          *    This option is NOT compatible with the [lineno] option.
-%%
-%%          * An option to include line numbers [lineno]. You must *run twice* for proper placement of the line numbers. 
-%%			*	 The lineno package does not number titles, footnotes, captions, or tables.
-%%          *    This option will disable balancing column height on final page if that option has been invoked.
-%%          *    The lineno package won't always number the lines preceding displayed math in a paragraph because
-%%          *    paragraph has not ended.  See that package's documentation for macros to address this problem, or
-%%          *    just leave a blank line above the displayed equation while you are editing and then remove the 
-%%          *    blank line and [lineno] option when you move to your final version.
-%%
-%%			* Options for PDF/A compliance. [pdf-a] will produce PDF/A-3u compliance with sRGB OutputIntent.
-%%			*	 [pdfapart= 1 or 2 or 3] and [pdfaconformance= b or u] can enable levels 1b, 2b, 2u, and 3b.
-%%			*    The most recent versions of LaTeX (2021 and later) are moving toward integrated support for pdf-a, 
-%%			*    through \DeclareDocumentMetadata{..}. The asmeconf class supports these new features, which can 
-%%			*	 replace the aforementioned class options. (An up-to-date LaTeX installation is required to use this.)
-%%
-%%          * Many options for calligraphic, script, and fraktur fonts from the mathalfa package; the
-%%          *    example shown here is: [mathalfa=cal=boondoxo] to use a Boondox font for \mathcal.
-%%          *    Some other options for cal are: dutchcal, zapfc, cm (default), euler,...
-%%          *    frak (fraktur), bb (blackboard bold), scr (script) may also be chosen this way.
-%%			*	 For details, refer to mathalfa documentation (at CTAN: http://ctan.org).
-%%
-%%          * Option to use superiors font from newtxtext for footnotes [nodefaultsups] and
-%%          *    for slightly larger small capitals, [largesc], also from newtxtext.
-%%
-%%          * An option to allow hyphenation of the typewriter font [hyphenate], from inconsolata package.
-%%          *    Hyphenation is normally suppressed for typewriter mode because it is often used for code.
-%%			*	 To replace the default variable word spacing by monospacing, use the option [mono].
-%%			*	 To get a zero without a slash, use [var0]
-%%
-%%          * Options (used by the babel package) to include passages in languages other than English (e.g., a translation 
-%%			*    of the abstract). Languages are called as options, e.g. [french], [spanish], [greek], [russian], etc. 
-%%			*    Language support is greatest when running LuaLaTeX with the [fontspec] option.
-%%			*    See Appendix B for details.
-%%
-%%  The use of commands defined or modified by the asmeconf class is illustrated throughout this file. In particular, 
-%%  ASME requires capitalized, sans-serif section headings, and as a result some care is needed when using macros 
-%%  in section headings, as also illustrated below.
-%%
-%%  Use an up-to-date and complete installation of LaTeX, such as TeX Live 2020 or later. Errors may occur with old set-ups.
-%%
- %=========================================================
-%% 
-%% LICENSE: 
-%%
-%% Copyright (c) 2022 John H. Lienhard
-%%
-%% Offered under the MIT license: https://ctan.org/license/mit 
-%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%% Class options are described above. Change these options as desired. 
-%%		If you are not using the language options, remove them (together with Appendices B and C)
-%%	 	Remove the [colorlinks] option before *final* submission to ASME, to get black text for printing,
-%%		but keep that option for other uses.
-
-\documentclass[balance,upint,subscriptcorrection,varvw,mathalfa=cal=boondoxo,pdf-a,colorlinks,nofoot]{asmeconf}
+\documentclass[balance,upint,subscriptcorrection,varvw,mathalfa=cal=boondoxo,pdf-a,nofoot]{asmeconf}
 \usepackage{tikz}
 \usetikzlibrary{shapes.geometric, arrows.meta}
-\tikzstyle{process} = [rectangle, minimum width=2cm, minimum height=1.3cm, text centered, draw=black]
+\tikzstyle{process} = [
+    rectangle, minimum width=2cm, minimum height=1.3cm, text centered, 
+    draw=black
+]
 \tikzstyle{arrow} = [thick,->,>={Stealth[scale=1.1]}]
@@
 \graphicspath{ {../data/} }
-%%%%%  pdf metadata  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\hypersetup{%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  pdf metadata  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\hypersetup{
 	pdfauthor={Yuanhao JIANG},
-	pdftitle={Mathematics of Reinforcement Learning with Applications to Quantitative Finance},
-	pdfkeywords={Reinforcement Learning,  Artificial Neural Networks},
-	pdfsubject={Describe Mathematics of Reinforcement Learning with Applications to Quantitative Finance},
+	pdftitle={
+        Mathematics of Reinforcement Learning with Applications to 
+        Quantitative Finance
+    },
+	pdfkeywords={
+        Reinforcement Learning,  Artificial Neural Networks, Quantitative 
+        Finance
+    },
+	pdfsubject={
+        Describe Mathematics of Reinforcement Learning with Applications to 
+        Quantitative Finance
+    },
     pdfurl={https://github.com/Yuanhao-JIANG/RL-in-QF},
-%	pdflicenseurl={https://ctan.org/pkg/asmeconf},
 }
@@
 \begin{document}
-% Change these fields to the right content for your conference.
-% You can comment these out if for some reason you don't want a header.
-% Use title case (first letters capitalized), not all capitals
-\ConfName{Proceedings of the ASME 2022\linebreak International Mechanical Engineering Congress and Exposition}
-\ConfAcronym{IMECE2022}
-\ConfDate{October 30--November 3, 2022} % update 
-\ConfCity{Columbus, OH} % update 
-\PaperNo{IMECE2022-XXXX}
+\title{
+    Mathematics of Reinforcement Learning with Applications to Quantitative 
+    Finance
+}
 
-% Units of measure (e.g., cm) and other specialty lowercase terms in the title should be 
-%   enclosed in \NoCaseChange{...} to maintain lower case type
-%   LaTeX will automatically set the rest of the title in all capital letters.
-
-\title{Mathematics of Reinforcement Learning with Applications to Quantitative Finance}
-%\title{Place Title Here: Place Subtitle After Colon}
-
-%   Put author names into the order you want. Use the same order for affiliations.
-%   \affil{#} tags the author's affiliation to the address in \SetAffiliation{#}.
-%   No space between last name and \affil{#}, separate names with commas.
-%
-%	For a sole author or a single affiliation for all authors, {#} may be left empty, as \affil{} and \SetAffiliation{} (but not with [grid] option!)
-%
-%   \CorrespondingAuthor{email} follows that author's affiliation, no spaces.  
-%   If multiple corresponding authors, put both email addresses in the same command and place after both authors.
-%
-%   \JointFirstAuthor, if applicable, follows the affiliation of the relevant authors, no spaces.
 \SetAuthors{
@@
 \SetAffiliation{1}{The University of Edinburgh, Edinburgh, UK}
-%	To switch from inline author names to gridded names, use the [grid] option.
 
@@
 
-%%% Change these to your keywords.  Keywords are automatically printed at the end of the abstract.
-%%% This command MUST COME BEFORE the end of the abstract.
-%%% If you don't want keywords, leave the argument of \keywords{} empty (or use the abstract* environment)
 \keywords{
@@
 
-%% Abstract should be 200 words or less
 \begin{abstract}
@@
     \end{tikzpicture}
-    \caption{MDP Illustration}
+    \caption{MDP Illustration~\cite{Sutton1998}}
     \label{fig:MDP-illustration}
@@
 \noindent By iteratively applying policy evaluation and policy improvement, we
-can obtain a sequence of monotonically improving policies and value functions:
+can obtain a sequence of monotonically improving policies and value 
+functions~\cite{Sutton1998} :
 \[\pi_0 \overset{E}{\longrightarrow} v_{\pi_0} \overset{I}{\longrightarrow}
@@
 \vspace{3mm}\newline We now truncate the policy evaluation such that it is
-stopped after just one sweep (one update of each state):
+stopped after just one sweep~\cite{Sutton1998} (one update of each state):
 \begin{align*}
@@
 
-\subsection{Generalized Policy Iteration}
+\subsection{Generalized Policy Iteration~\cite{Sutton1998}}
 \noindent As long as both processes, policy evaluation and policy improvement,
@@
 
-\subsection{Policy Gradient Methods}
+\subsection{Policy Gradient Methods~\cite{Sutton1998}}
 \noindent When the state space is arbitrarily large, we cannot find an optimal 
@@
 \begin{figure*}
-    \centering\includegraphics[scale=0.75]{a2c_out}
+    \centering\includegraphics[scale=0.7]{a2c_out}
     \caption{Training Result for Algorithm a2c}
@@
 \noindent To further show how Actor-Critic algorithm performs, we compare it 
-to another two popular algorithms: Reinforce 
+to another two popular algorithms: REINFORCE
 (Algorithm~\ref{algorithm:reinforce}) and PPO (Algorithm~\ref{algorithm:ppo}).
@@
 \begin{algorithm}
-    \caption{Reinforce for financial problem}\label{algorithm:reinforce}
+    \caption{Reinforce for financial problem~\cite{Sutton1998}}
+    \label{algorithm:reinforce}
     \begin{algorithmic}[1]
@@
 
-\begin{algorithm*}
-    \caption{PPO for financial problem}\label{algorithm:ppo}
+\begin{algorithm}
+    \caption{PPO for financial problem~\cite{SpinningUp2018}}
+    \label{algorithm:ppo}
     \begin{algorithmic}[1]
@@
         \EndFor
-        \Loop \hspace{0.3mm} (update multiple times)
+        \Loop \hspace{0.3mm} (update multiple times)\vspace{1mm}
+        \State \(r \gets \frac{\pi\left(c_t\middle|S_t, \bm{\theta}\right)}
+        {\pi\left(c_t\middle|S_t, \bm{\theta}_k\right)}\)\vspace{1.2mm}
+        \State \(L \gets \min{\left(
+                rA_t,
+                \text{clip}\left(r, 1-\epsilon, 1+\epsilon\right)A_t 
+        \right)}\)\vspace{1mm}
         \State \(\bm{\theta} \gets \underset{\bm{\theta}}{\text{arg\:max}}
         \frac{1}{|\mathcal{D}_k|T}
-        \sum_{\tau\in\mathcal{D}_k}^{} \sum_{t=0}^{T}
-        \min{\left(
-                \frac{\pi\left(c_t\middle|S_t, \bm{\theta}\right)}
-                {\pi\left(c_t\middle|S_t, \bm{\theta}_k\right)}A_t,
-                \text{clip}\left(
-                    \frac{\pi\left(c_t\middle|S_t, \bm{\theta}\right)}
-                    {\pi\left(c_t\middle|S_t, \bm{\theta}_k\right)},
-                    1-\epsilon, 1+\epsilon
-                \right)A_t
-        \right)}\)
+        \sum_{\tau\in\mathcal{D}_k}^{} \sum_{t=0}^{T} L\)
         \State \(\bm{w} \gets \underset{\bm{w}}{\text{arg\:min}}
@@
     \end{algorithmic}
-\end{algorithm*}
+\end{algorithm}
 
@@
 \begin{figure*}
-    \centering\includegraphics[scale=0.75]{out}
+    \centering\includegraphics[scale=0.7]{out}
     \caption{Training Result Comparison for Three Algorithm}
@@
 
-\section*{Acknowledgments}
-\noindent Place any acknowledgments here.
-
 %%%  REFERENCES  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2022-08-29 papers/paper_1-col.tex
Initial Commit

--- 2022-08-23 papers/paper_2-col.tex
@@
-\documentclass[balance,upint,subscriptcorrection,varvw,mathalfa=cal=boondoxo,pdf-a,nofoot]{asmeconf}
+\documentclass{article}
+\usepackage{arxiv}
+\usepackage{amsmath, amsfonts, bm, hyperref, siunitx, algorithm, algpseudocode}
+
 \usepackage{tikz}
@@
 \tikzstyle{arrow} = [thick,->,>={Stealth[scale=1.1]}]
-\usepackage{algorithm, algpseudocode}
-\usepackage{siunitx}
+
+\usepackage{graphicx}
 \graphicspath{ {../data/} }
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  pdf metadata  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \hypersetup{
@@
     },
-    pdfurl={https://github.com/Yuanhao-JIANG/RL-in-QF},
 }
@@
 }
-
-\SetAuthors{
-	Yuanhao JIANG\affil{1}\CorrespondingAuthor{s2132254@ed.ac.uk}
+\author{
+    Yuanhao JIANG\thanks{
+        Current student at the University of Edinburgh.
+    } \\
+	School of Mathematics\\
+	The University of Edinburgh\\
+	Edinburgh, UK \\
+	\texttt{s2132254@ed.ac.uk} \\
 }
 
-\SetAffiliation{1}{The University of Edinburgh, Edinburgh, UK}
-
 \maketitle
-
-\keywords{
-    Reinforcement Learning, Artificial Neural Networks, Quantitative Finance
-}
 
@@
 \end{abstract}
+
+\keywords{
+    Reinforcement Learning \and 
+    Artificial Neural Networks \and 
+    Quantitative Finance
+}
 
@@
 
-\subsection{Generalized Policy Iteration~\cite{Sutton1998}}
+\subsection{Generalized Policy Iteration}
 \noindent As long as both processes, policy evaluation and policy improvement,
 continue to update all states, the ultimate result is typically the 
-same --- converge to the optimal value function and an optimal policy.
+same --- converge to the optimal value function and an optimal 
+policy~\cite{Sutton1998}.
 \vspace{3mm}\newline Generalized policy iteration (GPI) is used to refer to the
 general idea of letting policy evaluation and policy improvement interact,
-independent of the granularity of the two processes (instead of letting each
-complete before the other begins).
+independent of the granularity of the two processes~\cite{Sutton1998} 
+(instead of letting each complete before the other begins).
 
@@
 \begin{align*}
-    &[v_\pi(S_t)]_{k+1} \\
-    =\:& \frac{1}{k}\sum_{i=1}^{k} G_i\\
+    [v_\pi(S_t)]_{k+1} =& \frac{1}{k}\sum_{i=1}^{k} G_i\\
     =\:& \frac{1}{k}\left(G_k + \sum_{i=1}^{k-1} G_i\right)\\
@@
 
-\subsection{Policy Gradient Methods~\cite{Sutton1998}}
+\subsection{Policy Gradient Methods}
 \noindent When the state space is arbitrarily large, we cannot find an optimal 
@@
 without consulting a value function. A value function may still be used to
-learn the policy parameter, but is not required for action selection.
+learn the policy parameter, but is not required for action 
+selection~\cite{Sutton1998}.
 \vspace{3mm}\newline We use \(\bm{\theta}\) and \(\bm{w}\) to denotes the
@@
 including normal distribution, binomial distribution, and so on. For example, 
-a feature vector \(x\) is described as Table \ref{tab:1}
-\begin{table*}
-    \caption[Table]{Customer Feature Vector Description\label{tab:1}}
+a feature vector \(x\) is described as Table \ref{tab:feature-vector}
+\begin{table}
+    \caption[Table]{
+        Customer Feature Vector Description\label{tab:feature-vector}
+    }
     \centering
@@
     \end{tabular}
-\end{table*}
+\end{table}
 
@@
 generated data set with each observation is a customer's features followed by 
-a price, then followed by a resopnse, as illustrated by Table \ref{tab:2}.
-\begin{table*}
-    \caption[Table]{Customer Feature Vector Description\label{tab:2}}
+a price, then followed by a resopnse, as illustrated by 
+Table \ref{tab:response}.
+\begin{table}[H]
+    \caption[Table]{
+        Customer Resopnse Examples\label{tab:response}
+    }
     \centering
@@
 of both function is the state, as illustrated in Figure~\ref{fig:ANN}.
-\begin{figure*}
+\begin{figure}[H]
     \centering
@@
     \caption{ANN model for policy and value function\label{fig:ANN}}
-\end{figure*}
+\end{figure}
 where \(n(S)\) denotes the vector length of the state and \(n(A)\) denotes 
@@
 \(\gamma=0.99\), \(\alpha_\theta=\alpha_{\bm{w}}=\num{3e-4}\).
-\begin{figure*}
-    \centering\includegraphics[scale=0.7]{a2c_out}
+\begin{figure}
+    \centering\includegraphics[scale=0.65]{a2c_out}
     \caption{Training Result for Algorithm a2c}
     \label{fig:a2c-out}
-\end{figure*}
+\end{figure}
 The graph shows that the moving average reward converges within only 50
@@
         \Loop \hspace{0.3mm} (update multiple times)\vspace{1mm}
-        \State \(r \gets \frac{\pi\left(c_t\middle|S_t, \bm{\theta}\right)}
-        {\pi\left(c_t\middle|S_t, \bm{\theta}_k\right)}\)\vspace{1.2mm}
-        \State \(L \gets \min{\left(
-                rA_t,
-                \text{clip}\left(r, 1-\epsilon, 1+\epsilon\right)A_t 
-        \right)}\)\vspace{1mm}
         \State \(\bm{\theta} \gets \underset{\bm{\theta}}{\text{arg\:max}}
         \frac{1}{|\mathcal{D}_k|T}
-        \sum_{\tau\in\mathcal{D}_k}^{} \sum_{t=0}^{T} L\)
+        \sum_{\tau\in\mathcal{D}_k}^{} \sum_{t=0}^{T}
+        \min{\left(
+                \frac{\pi\left(c_t\middle|S_t, \bm{\theta}\right)}
+                {\pi\left(c_t\middle|S_t, \bm{\theta}_k\right)}A_t,
+                \text{clip}\left(
+                    \frac{\pi\left(c_t\middle|S_t, \bm{\theta}\right)}
+                    {\pi\left(c_t\middle|S_t, \bm{\theta}_k\right)},
+                    1-\epsilon, 1+\epsilon
+                \right)A_t
+        \right)}\)
         \State \(\bm{w} \gets \underset{\bm{w}}{\text{arg\:min}}
@@
 \(\epsilon=0.5\) (if applicable).
-\begin{figure*}
-    \centering\includegraphics[scale=0.7]{out}
+\begin{figure}
+    \centering\includegraphics[scale=0.65]{out}
     \caption{Training Result Comparison for Three Algorithm}
     \label{fig:3-algorithms-out}
-\end{figure*}
+\end{figure}
 As we can see, the Actor-Critic algorithm converges the fastest, within 50 
@@
 
-%%%  REFERENCES  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%
-%% Put your references into your .bib file in the usual way. Run latex once, bibtex once, then latex twice.
-%% The asmeconf.bst style allows @inproceedings and @proceedings to include: 
-%%		venue = {Location of Conference}, 
-%%		eventdate = {Month, days},
-
-\nocite{*}%% <=== Delete this line unless you want to typeset the entire contents of your .bib file!
-
-\bibliographystyle{asmeconf}  %% .bst file following ASME conference format. Do not change.
-\bibliography{paper_2-col}
+\bibliographystyle{plain}
+\bibliography{references}
 

### 2022-08-29 papers/paper_2-col.tex
regenerate references
fix table name typo

@@
 including normal distribution, binomial distribution, and so on. For example, 
-a feature vector \(x\) is described as Table \ref{tab:1}
+a feature vector \(x\) is described as Table \ref{tab:feature-vector}
 \begin{table*}
-    \caption[Table]{Customer Feature Vector Description\label{tab:1}}
+    \caption[Table]{
+        Customer Feature Vector Description\label{tab:feature-vector}
+    }
     \centering
@@
 generated data set with each observation is a customer's features followed by 
-a price, then followed by a resopnse, as illustrated by Table \ref{tab:2}.
+a price, then followed by a resopnse, as illustrated by 
+Table \ref{tab:response}.
 \begin{table*}
-    \caption[Table]{Customer Feature Vector Description\label{tab:2}}
+    \caption[Table]{Customer Resopnse Examples\label{tab:response}}
     \centering
@@
 \bibliographystyle{asmeconf}  %% .bst file following ASME conference format. Do not change.
-\bibliography{paper_2-col}
+\bibliography{references}
 

### 2022-08-30 papers/paper_1-col.tex
reformat some equations
add reference and bibliography

@@
 \usepackage{arxiv}
+\usepackage{cite}
 \usepackage{amsmath, amsfonts, bm, hyperref, siunitx, algorithm, algpseudocode}
@@
 
+\tableofcontents
+
 \section{Introduction}
@@
 \noindent The reinforcement learning method we want to use is based on the Markov 
-decision process (MDP), as illustrated in Figure~\ref{fig:MDP-illustration}.
-\begin{figure}
+decision process (MDP)~\cite{Sutton1998, menache2005basis}, as illustrated in 
+Figure~\ref{fig:MDP-illustration}.
+\begin{figure}[H]
     \centering
@@
 improve it accordingly. To do this, we introduce the q-function under 
-policy \(\pi\)
+policy \(\pi\)~\cite{Sutton1998}
 \[q_\pi(s, a) = \mathbb{E}\left[R_{t+1} + \gamma v_\pi(S_{t+1})\;\middle|\;
@@
 policy~\cite{Sutton1998}.
-\vspace{3mm}\newline Generalized policy iteration (GPI) is used to refer to the
-general idea of letting policy evaluation and policy improvement interact,
-independent of the granularity of the two processes~\cite{Sutton1998} 
-(instead of letting each complete before the other begins).
+\vspace{3mm}\newline The general idea of alternating policy evaluation and 
+policy improvement, independent of the frequency and convergence of the two 
+processes~\cite{Sutton1998} (instead of letting each complete before the other 
+begins) is called Generalized Policy Iteration (GPI).
 
@@
 estimate the value function from only experience. There are two methods to do 
-so: Monte Carlo Methods and Temporal-Difference. We will use 
-Temporal-Difference method in this project.
+so: Monte Carlo Methods and 
+Temporal-Difference 
+Method~\cite{menache2005basis, sutton1988learning, Sutton1998}. We will use 
+Temporal-Difference method (more specifically, the TD(0) method, which 
+converges to the maximum likelihood estimate of the function we 
+estimate~\cite{sutton1988learning}) in this project, since the Monte Carlo 
+methods might have higher variance than Temporal-Difference 
+method~\cite{hambly2021recent, franccois2019overfitting, von2011statistical}.
 \vspace{3mm}\newline To estimate \(v_\pi(S_t)\) using only the experience, we 
@@
 with \(\alpha\) being the stepsize. And this also applies to the q function:
-\begin{multline*}
-    q_\pi(S_t, A_t)\longleftarrow q_\pi(S_t, A_t)\\
-    +\alpha[R_{t+1}+\gamma q_\pi(S_{t+1}, A_{t+1})-q_\pi(S_t, A_t)]
-\end{multline*}
+\[q_\pi(S_t, A_t)\longleftarrow 
+q_\pi(S_t, A_t)+\alpha[R_{t+1}+\gamma q_\pi(S_{t+1}, A_{t+1})-q_\pi(S_t, A_t)]\]
 
@@
 \subsubsection{The Policy Gradient Theorem}
-The policy gradient theorem says
+The policy gradient theorem~\cite{sutton1999policy} says
 \[\nabla J(\bm{\theta})\propto \sum_{s} \mu(s)
@@
 
-\subsubsection{Actor-Critic Methods}
+\subsubsection{Actor-Critic Methods}\label{Actor-Critic Methods}
 Recall the TD method, we make use of 
@@
 S_t=s, A_t=a\right]\), by taking one sample estimate, and choosing
-\(\hat{v}(S_t, \bm{w})\) as baseline, we have
+\(\hat{v}(S_t, \bm{w})\) as baseline~\cite{Sutton1998}, we have
 \[\nabla J(\bm{\theta})\propto\mathbb{E}_\pi\left[
@@
 \end{align*}
-The actor-critic method is based on the above updates formulas, details are
-shown in Algorithm \ref{algorithm:actor-critic}.
+The actor-critic method based on the above updates formulas, updating policy
+parameter \(\bm{\theta}\) and value function weight \(\bm{w}\) simultaneously 
+at each time step, is called two time-scale (natural) actor-critic 
+algorithms~\cite{xu2020non, hambly2021recent}, details of the algorithm itself 
+are shown in Algorithm \ref{algorithm:actor-critic}~\cite{Sutton1998}.
 \begin{algorithm}
@@
 Table \ref{tab:response}.
-\begin{table}[H]
+\begin{table}
     \caption[Table]{
@@
         \left(\text{pt}_i-\bar{\text{pt}}\right)^2}{3}\]
-        Later we use this to compute reward to 
+        \vspace{1mm}Later we use this to compute reward to 
         make sure the agent will promote to all types of customers instead of 
@@
 policy and the value function. In this project we use artificial neuro networks
-(ANNs) as the parameterized policy and value function, each with three linear 
-layers, and with the ReLU function as the activation function. And the input 
-of both function is the state, as illustrated in Figure~\ref{fig:ANN}.
-\begin{figure}[H]
+(ANNs) to parameterize our policy and value function as it suits well on 
+algorithms like Actor-Critic, REINFORCE, PPO and so on (for details see 
+\cite{wang2019neural, liu2019neural}). Each of our ANNs has three linear 
+layers, with the ReLU function as the activation function. And the input of 
+both function is the state, as illustrated in Figure~\ref{fig:ANN}.
+\begin{figure}
     \centering
@@
 \subsection{The Algorithm}
-\noindent Algorithm \ref{algorithm:actor-critic-fin} uses RL with actor-critic 
-method, and with the help of what we have built in previous sections, to solve 
-the problem.
+\noindent Algorithm \ref{algorithm:actor-critic-fin} uses (two time-scale) 
+actor-critic method~\cite{xu2020non, hambly2021recent, Sutton1998}, and with 
+the help of what we have built in previous sections (especially 
+subsection~\ref{Actor-Critic Methods}), to solve the problem.
 \begin{algorithm}
@@
 \noindent To further show how Actor-Critic algorithm performs, we compare it 
-to another two popular algorithms: REINFORCE
-(Algorithm~\ref{algorithm:reinforce}) and PPO (Algorithm~\ref{algorithm:ppo}).
+to another two popular algorithms: REINFORCE~\cite{williams1992simple}
+(Algorithm~\ref{algorithm:reinforce}) and PPO~\cite{schulman2017proximal} 
+(Algorithm~\ref{algorithm:ppo}).
 The policy function of the two algorithms is implemented the same way as we 
@@
 In the mean time, the slow convergence for PPO algorithm is expected since it 
-uses a clamp function to prevent model from changing too fast in a single 
-update, although at current stage it seems to be unnecessary for our specific 
-problem setup. 
+uses a clip function to prevent model from changing too fast in a single 
+update~\cite{schulman2017proximal, SpinningUp2018}, although at current stage 
+it seems to be unnecessary for our specific problem setup. 
 Further investigation needs to be done for the unexpected small drop of the 
@@
 
-\bibliographystyle{plain}
+\bibliographystyle{unsrt}
 \bibliography{references}
